---
title: "Self-critical rumination - A network approach"
bibliography: rumination.bibtex
csl: apa7.csl
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# libraries declared
library(tidyverse)
library(networktools)
library(qgraph)
library(glasso)
library(ggraph)
library(igraph)
library(bootnet)
library(modelr)
library(scales)
library(knitr)
library(ggpubr)
library(broom)
library(ergm)
library(fdrtool)
library(eigenmodel)
library(ROCR)
source("R/data_import.R")
source("R/functions.R")
# data import
source("../networks_with_r/get_rumi.R")
suppressMessages(extrafont::loadfonts(device='postscript'))
setwd('../networks_with_r')
source("get_rumi.R")
source("src/functions.R")
setwd('/home/tamas/repos/rumination_lasso')
```

## 2. Methods

### Hypothesis and the use of Network Analysis
*Psychological networks* have their own characteristics which differentiate them from other networks of the graph theory [@Epskamp2017; @Newman2010]. 
Nodes usually represent some psychological measures or items of a psychological assessment tool, while the edges of the network reflect the corresponding estimates of association derived from the data.
Having two rumination-related questionnaires, we assumed

* network analysis will reveal their respective internal structure previously established in the literature (RRS having a two-scale structure: reflection and brooding; while SCRS will show a single-scale structure);
* on the other hand, we hypothesized that in their common network, items overlapping in scope will change these clear outlines of the two measurement tools. According to our hypothesis, items of the RRS scale 'brooding' will have non-trivial association with the self-critical aspects of rumination;
* thus, we also assumed a combined rumination network, representing the generic (more trait-like) and the self-critical aspects of rumination will exhibit a three-component structure.

<!-- Sample sizes have direct impact on estimated accuracy and stability of the psychological network, thus the accuracy of the network parameters and measures is crucial: By obtaining robust results we can have a more realistic picture of a network without knowing the true network shape and structure. --> 
<!-- Just like any other psychological variables, network characteristics are also sensitive to sampling, estimation methods, included variables, outliers and various other components of an analysis. --> 
<!-- As [@Epskamp2017a] points out, psychological networks differ from *reflective latent variable models* by not seeking for a common cause of co-occurrence of variables (such as symptoms or different items of a questionnaire), but instead their focus is on quantifying and visually show the multivariate dependencies and the different pathways of direct relationships between the nodes. --> 
<!-- A major conceptual difference emerges from the network perspective for psychological data: psychological variables, such as symptoms, states, attitudes and other constructs (represented as nodes) have direct impact on each other, and are not caused by some latent variables.  [@Epskamp_2018]. --> 
In the current study, we used a fairly large sample of indiviuals (N=`r nrow(rumi_data)`) to construct a dense, undirected network of rumination-related psychological constructs. 
The vertices represent the items of the Ruminative Response Style (RRS) and the Self-critical Rumination Scale (SCRS), while edges are penalized partial correlations (using LASSO penalization, [@Friedman2007] ).


### 2.1. Least Absolute Shrinkage and Selection Operator (LASSO)

We constructed individual and combined networks of RRS and SCRS with respective penalized correlation matrices using the *EBICglasso* function of the **qgraph** package (number of lambda parameters were set to 1000).
In order to shrink the edges, achieve high specificity, and get a less dense network, we let the function to exclude any elements of the underlying precision matrix below a threshold value (*threshold* parameter set to TRUE).

The LASSO uses L1 regularization([@Tibshirani1996], [@Friedman2007]), and in the current study, it results in a partial correlation network where edges represent direct associations between pairs of items, while the influence of all other items in the network are kept controlled. 
The regularization by L1 penalty ensures that trivially small partial correlations are set to zero [@McNally_2017], thus ensure a *sparse* network which are more interpretable (@Epskamp_2018). 

The tuning parameter of *gamma* in the graphical LASSO algorithm has been set to 0.5 value in accordance with [@McNally_2017] and [@Bernstein2019] in order to achieve sparse graphs. 
The final networks were chosen by the lowest values of the *extended Bayesian Information Criterion* (EBIC).

<!-- Before going further into network modeling, we estimated the 95% confidence intervals of network centrality measures to have an understanding of the sampling distribution of our estimates. According to @Epskamp2017a low sample size and non-regularized estimates might lead to amplify any bootstrap bias; by having a larger sample of individuals, we expect lesser levels of bias of any bootstrap estimates for network accuracy and stability. -->

### 2.2 Redundant items

We applied the *goldbricker* function from the R package *networktools* [@Jones2017] in order to search for pairs of items in the RRS, SCRS and their combined networks that were highly correlated (r > 0.75) and exhibited the same pattern with other items. 


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dataset <- rumi_data
var_names <- names(dataset)
```
After the LASSO regularization no further dimensionality reduction was necessary based upon the *goldbricker* evaluation.
As subject for this paper,


### 2.3 Network descriptives

A comparative overview of the three networks was produced with their descriptives (degree distribution) and their centrality measures (strength, closeness, betweenness; [@GaborCsardi2020]), their One- and Two-Step Expected Influence (EI) measures ([@Robinaugh2016], [@Heeren2018]).
In order to further elaborate the question of vertex importance, we identified *bridge nodes* using the functions provided by the *networktools* R package [@Jones2017]. 
We estimated both one-step and two-step bridge expected influence measures which reflect the sum of edge weights connecting one vertex to other groups on vertices (or communities); and also express a vertex's secondary influence on the rest of the network, respectively. 
Higher influence scores indicate that a certain node is more likely to active neighbouring nodes, subgroups of nodes or communities.
In order to estimate the Expected Influence metrics, we used the *expectedInf* function of the *networktools* R package.
Using the *networktools* R library bridge expected influence measure were estimated for the two questionnaires we used in this study.

### 2.4. Community detection
In order to get an understanding of community of vertices and to see if vertices can be grouped into neighbourhoods corresponding to the previously established sub-scale structure of RRS, SCRS and investigate their separation in their combined network, we used the community detection methods of the *igraph* R package. 
When detecting possible communities of vertices, we utilized previous insights [@Reichardt2006; @Bernstein2019, @GaborCsardi2020].
In order to mitigate the effect of choice of community detection algorithms we performed more of them available in the *igraph* package multiple times.

### 2.5. Network accuracy and stability
Accuracy and stability have an important role in estimating network parameters when samples might vary in characteristics and size [@Epskamp2017; @Epskamp2017a]. 
One way of estimating network accuracy is to produce a 95% confidence interval of edge-weights with some variant of bootstrap. 
In our case we chose the non-parametric bootstrap estimate for sake of interpretability, where the penalized partial correlation coefficients formed the edge weights. 
Network stability is quantified with the *Correlation Stability* (CS-coefficient): an estimate of the maximum proportion of cases that can be dropped (with 95% certainty) to retain a correlation with the original centrality higher than some fixed threshold value (in the present paper, 0.7). 
Simulation studies [@Epskamp2017] lead us in our expectation as the CS-coefficient should be between 0.25 and 0.5. 


 
## 3. Results

### 3.1 Network descriptives

The undirected, weighted, associational networks of RRS, SCRS and their combined structure can be seen on Figure 1. below.
All three networks proved to be connected (any vertex is reachable from every other).
Vertices represent the corresponding items of each questionnaire with labels showing item number, sub-scale and a label for each item.
Sub-scales are presented in a colour-coded fashion as the outer circle of each vertex.
Edges are the LASSO (L1)-penalized partial correlation coefficients whose value is represented as shade and width of the arcs.

The RRS (order of `r vcount(RRS_graph)`, size of `r ecount(RRS_graph)`) and SCRS (order of `r vcount(SCRS_graph)`, size of `r ecount(SCRS_graph)`) networks are densely connected networks.
While SCRS exhibits no *articulation point* (also call *cut vertex* whose removal would disconnect the network [@GaborCsardi2020]), the vertex of the *'problem'* item of RRS acts as an articulation point, as it would cut off the *'deserve'* vertex.
Articulation points are marked with * on Figure 1.

The combined network (order: `r vcount(rumi)`, size: `r ecount(rumi)`) has no articulation points.
In order to analyze their respective internal structures, we performed community detection using the *igraph* package in R.
Inner node point of each vertex provide colour coding for our community detection results (the presented certainty percentages are True Positive Rates of each sub-scale).


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
i  <- 1000
# simulate_communities(RRS_graph, path="output/RRS_communities.RDS",i=i)
# simulate_communities(SCRS_graph, path="output/SCRS_communities.RDS",i=i)
# simulate_communities(rumi, path="output/combined_communities.RDS",i=i)
RRS_simulated_communities <- readRDS("output/RRS_communities.RDS")
SCRS_simulated_communities <- readRDS("output/SCRS_communities.RDS")
combined_simulated_communities <- readRDS("output/combined_communities.RDS")

# RRS_item_TPR <- item_level_TPR(RRS_simulated_communities, RRS_graph, threshold=0.95)
# saveRDS(RRS_item_TPR, 'output/RRS_item_TPR.RDS')
# SCRS_item_TPR <- item_level_TPR(SCRS_simulated_communities, SCRS_graph, threshold=0.5)
# saveRDS(SCRS_item_TPR, 'output/SCRS_item_TPR.RDS')
# combined_item_TPR <- item_level_TPR(combined_simulated_communities, rumi)
# saveRDS(combined_item_TPR, 'output/combined_item_TPR.RDS')
RRS_item_TDR <- readRDS('output/RRS_item_TPR.RDS')
SCRS_item_TDR <- readRDS('output/SCRS_item_TPR.RDS')
combined_item_TDR <- readRDS('output/combined_item_TPR.RDS')
accuracy_rrs  <- readRDS("output/accuracy_rrs.RDS")
accuracy_scrs  <- readRDS("output/accuracy_scrs.RDS")
accuracy_combined <- readRDS("output/accuracy_combined.RDS")
accuracy_rrs <- network_accuracy_data(accuracy_rrs)
accuracy_scrs <- network_accuracy_data(accuracy_scrs)
accuracy_combined <- network_accuracy_data(accuracy_combined)

get_itemnames <- function(namevector){
    grid <- tibble(expand.grid(namevector, namevector))
    grid <- grid %>% filter(!Var1==Var2)
    grid


}
# add accuracy to networks
rumi <- add_accuracy_to_graph(rumi, accuracy_combined)
RRS_graph <- add_accuracy_to_graph(RRS_graph, accuracy_rrs)
SCRS_graph <- add_accuracy_to_graph(SCRS_graph, accuracy_scrs)

overalltextsize <- 24
textsize=5
RRS_plot <- beautify(RRS_graph, RRS_simulated_communities, title="RRS undirected graph", no_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize,item_TDR=RRS_item_TDR)
SCRS_plot <- beautify(SCRS_graph, SCRS_simulated_communities, title="SCRS undirected graph", no_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize,item_TDR=SCRS_item_TDR)
combined_plot <- beautify(rumi, combined_simulated_communities, title="RRS & SCRS undirected graph",force_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize, item_TDR=combined_item_TDR)
network_plot <- ggarrange(ggarrange(RRS_plot, SCRS_plot, nrow=2,heights=c(1,1)), combined_plot, widths=c(0.95,1.05))
# ggsave("output/networkplot.png",network_plot, dpi=400, device='png',width=27, height=14)

# RRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# SCRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# combined_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
RRS_tpr <- suppressMessages(get_TPR(RRS_simulated_communities,RRS_graph))

RRS_tpr_s <- suppressMessages(RRS_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

SCRS_tpr <- suppressMessages(get_TPR(SCRS_simulated_communities,SCRS_graph))
SCRS_tpr_s <- suppressMessages(SCRS_tpr %>% 
    group_by(Subscale, Method, Weights)  %>%
    summarise(TPR_m = mean(TPR)))

combined_tpr <- suppressMessages(get_TPR(combined_simulated_communities,rumi))
combined_tpr_s <- suppressMessages(combined_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

combined_tpr_top <- suppressMessages(combined_tpr %>% 
    filter(!Method %in% c("walktrap", "optimal","fast_greedy")) %>%
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))



# summary table 
seed <- 647
weights <- TRUE
method <- 'optimal'
summary_table <- bind_rows(network_summary(RRS_graph, name="RRS",seed=seed,method=method,weights=weights, item_TPR=RRS_item_TDR),
                            network_summary(SCRS_graph, name="SCRS", seed=seed,method=method,weights=weights, item_TPR=SCRS_item_TDR),
                            network_summary(rumi, name="Combined",seed=seed,method=method,weights=weights, item_TPR=combined_item_TDR))

```

\newpage
\blandscape

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE,fig.retina=1,fig.align='center', fig.width=32, fig.height=20, fig.cap='Tableau view of three graphs of rumination'}
network_plot
```

\elandscape

As the choice of algorithm has non-trivial impact on the identified community structure, after having selected the *"optimal"*, the *"spinglass"*, the *"walktrap"* and (to also include hierarchical clustering) the *"fast greedy"* methods, we tested each a `r i` times on the three networks.
We also provided an edge weight vector in the form of the LASSO-penalized partial correlation coefficients (or alternatively, omitted weights).

The RRS two-scale structure could be recreated with all four algorithms with the inclusion of the weight vector not having effect on the measures.
For the sub-scale of *brooding* the average **true positive rate** (TPR) was `r RRS_tpr_s[1,2][[1]]`; for *reflection*  `r round(RRS_tpr_s[2,2][[1]],3)`.
In case of the *reflection* subscale, lower average TPR becomes tangible with the inspection of items 2 (*"analyze"*) and 9 (*"person"*) whose low TPR indicates that depending in the choice of community detection they have a chance of forming their own community or being classified as members of the *brooding* scale.


In the case of SCRS, the best TPR of `r SCRS_tpr_s[7,4][[1]]` has been achieved with `r SCRS_tpr_s[7,2][[1]]` community detection.
The one-scale structure of the SCRS has been reestablished in these results, too.

The combined rumination network shows a clear expected structure, with having high TPR for each sub-scale (on average, *brooding* (`r combined_tpr_s[1,2][[1]]`), *reflection* (`r combined_tpr_s[2,2][[1]]`) and *self-critical* (`r combined_tpr_s[3,2][[1]]`)).
Commenting on the stability of the network community structure the RRS *reflection* sub-scale exhibits strong TPR rates, and the weakness of the two items from their respective stand-alone network for items 2 and 9 are no longer present in the combined graph.
The RRS *brooding* scale has good separation in terms of TPR, except for its item 3 (*#react#*) having <0.9 TPR.
The one-scale SCRS has also a separable community with high (>0.925) TPR.
Keeping only the *spinglass* algoritm (as used by [@Bernstein2019]), we get high average 1.0 TPR for the combined graph.

Please refer to our summary table in the Appendix (Table 1.) for actual descriptives and identified communities using the *spinglass* method.
Please note where it was meaningful (i.e., with influence measures) we standardized the scores.

### 3.2 Internal Structure with an exponential random graph model

In order to measure the impact of tools (RRS, SCRS) and their respective scales (*brooding*, *reflection* and *self-critical*) on network structure, we constructed an *exponential random graph model* (ERGM).
In the model of our combined network, endogenous (network structure related) predictors included the number of edges in the network (*edges* member), and a generalization of triadic structures based on alternating sums of *k-triangles* [@Hunter2007; @Goodreau2009] to involve some higher-order global network structures as a reflection on **clustering** in the form of completed triangles of vertices.
In order to capture exogenous effects (i.e., vertex attributes), we added *tool* and *sub-scale * as predictors, especially testing for *homophily* (assuming that belonging to the tool and its scale will increase the log-odds of being connected by an edge).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ergm_model_fit <- readRDS("output/ergmfit.RDS")
anova_tidy <- broom::tidy(anova(ergm_model_fit))
ergm_tidy <- broom::tidy(ergm_model_fit)
names(ergm_tidy) <- c("Term", "Estimate", "Std. Error", "MCMC Error %", "Statistic", "p")
ergm_tidy[2,1] <- 'GWESP [triangle]'
knitr::kable(ergm_tidy,digits=3,label="", caption="ERGM model fit results with Markov chain Monte Carlo Maximum Likelihood Estimation")

# gof(ergm_model_fit)
# mcmc.diagnostics(ergm_model_fit)
```

An ANOVA analysis on the overall model indicates (with df=`r anova_tidy$df[2][[1]]`, Residual Deviance=`r round(anova_tidy$Resid..Dev[2][[1]],3)`, p=`r round(anova_tidy$Pr...Chisq..[2][[1]],4)`) that variables involved in the model explain the network connectivity in a highly non-trivial fashion.
The detailed analysis reveals that endogenous effects decrease the log-odds of connectivity in the case of number of *edges* (by `r round(exp(ergm_tidy$Estimate[1][[1]]),3)`) and at p<0.05 level the closed triangle formulation (log-odds decreased by `r round(exp(ergm_tidy$Estimate)[2][[1]],3)`) indicates a non-trivial negative impact on clustering.
As expected, exogenous effects, such as sub-scale have a significant positive impact on connectivity (log-odds effects: tool (sub-scale: (`r round(exp(ergm_tidy$Estimate[5][[1]]),3)`)).

### 3.3 Association Network Inference

In order to test for non-zero edges in our network, we used a data-driven method to assess the null distribution of partial correlation coefficients used during network creation.
The R package **fdrtool** allowed us to model the probability density function $\eta_0$, the fraction of true null hypotheses in the data; (1-$\eta_0$) for the true alternative hypotheses.
The mixture model for some statistic S thus takes the following form (where in our analysis, S is the partial correlation coefficient).

\begin{center}
$\ f(S)=\eta_0 f_0(S) + (1-\eta_0) f_1(S)$
\end{center}

To apply adjustment due to the number of performed tests, we applied the *False Discovery Rate* (FDR) to the *p*-values (the rate of false rejections against the number of rejections).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=6,fig.height=6, fig.align='center', fig.cap="Association Network Inference results"}
mute <- function(exp) {
  invisible(capture.output(exp))
}
mycorr <- cor_auto(rumi_data, detectOrdinal = TRUE)
mycorr <- cor(rumi_data, method = "spearman")
mycorr <- mycorr[upper.tri(mycorr)]
mute(fdr <- suppressWarnings(fdrtool(mycorr, statistic = "correlation")))
```
The low $\eta_0$ (`r round(unname(unlist(fdr['param'])[3]),3) `) indicates large mixing rate for the alternative hypothesis of edges having non-zero weights.
The histogram of absolute correlation coefficients estimated using the data (alternative component) has a centered shape in contrast to the null component.
The density-based FDR drops once empirical correlations reach $\rho$=0.1.



### 3.4 Latent Network Modeling

We constructed an eigenmodel to further explore the structure of the combined graph of RRS and SCRS.
Our expectation was that sub-scales will have non-trivial impact on the resulting eigenvalues.
By applying eigenvalue decomposition, we obtained the first two eigenvectors and used them to plot the vertices.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=10, fig.height=8, fig.cap="Vertices of the combined graph by the first two eigenvalues"}
fitEM <- readRDS("output/fitEM.RDS")
evals <- colMeans(fitEM$L_postsamp)
evecs <- eigen(fitEM$ULU_postmean)$vec[, 1:2]
subscale <- c("Brooding", "Reflection", "Brooding", "Reflection", "Reflection", "Brooding", "Brooding", "Brooding", "Reflection", "Reflection", rep("Self-critical", 10))
toolnames <- c(rep("RRS", 10), rep("SCRS", 10))
itemnames <- c(paste0("RRS_", 1:10), paste0("SCRS_", 1:10))
toollookup <- data.frame(item = V(rumi)$name, label = V(rumi)$label)
labels <- c()
for (item in seq_along(itemnames)) {
    label <- toollookup[toollookup$item == itemnames[item], ]$label
    item_name <- paste0(paste0(strsplit(itemnames[item],"_")[[1]], collapse="("),")")
    labels[item] <- paste0(item_name, "\n", label)
}
plot_eigen(evecs, evals, rumi_graph, toolnames, subscale, labels)
```

Our visual insight from *Figure 3.* is that the first eigenvector servers as a separator between RRS and SCRS having a posterior mean of $\bar{ev_1}$=`r round(evals[1],3)`.
The second eigenvector seems to separate between the upper half of the two-dimensional space of SCRS and the *brooding* scale, and the lower half being the *reflection* scale ($\bar{ev_2}$=`r round(evals[2],3)`).

In order to test the goodness-of-fit of the eigenmodel, using *k*-fold cross-validation (k=5), we refitted the model to a subset of the original data, using the complement 1/5 fraction for predicting the elements of the adjacency matrix of our original network.

For this part of the analysis, we defined three conditions in the eigenmodel on top of the original model.
In the first iteration we used the eigenmodel without the regression component defining the adjacency matrix as function of only the pairwise latent effects summarized in the following matrix.

\begin{center}
$\ Y_{ij}=f(u_i \Lambda u_j) $
\end{center}

In the second and third iterations, we defined an optional regression model in addition to the pairwise latent effects, where $\textbf{x}_{ij}$ is a pair-specific predictor vector.
This extends our model to the following equation.

\begin{center}
$\ Y_{ij}=f(\beta^{'} x_{ij} +  u_i \Lambda u_j) $
\end{center}

Thus, in the second iteration we cross-validated an extended eigenmodel with the tool (RRS or SCRS) as nominal grouping factor of vertices playing the predictor role.
And in the same manner, the third iteration tested a model with the scales of *brooding*, *reflection* and *self-critical* serving as pair-wise covariate predictor effects.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
A <- as_adjacency_matrix(rumi, sparse = FALSE)
Avec <- A[lower.tri(A)]
Avec.pred1 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred1.RDS")
Avec.pred2 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred2.RDS")
Avec.pred3 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred3.RDS")

getAUC <- function(x, condition) {
    y <- slot(x, "y.values")[[1]]
    x <- slot(x, "x.values")[[1]]
    Condition <- rep(condition, length(y))
    data.frame(x, y, Condition)
}

pred1 <- prediction(Avec.pred1, Avec)
perf1 <- performance(pred1, "tpr", "fpr")
pred2 <- prediction(Avec.pred2, Avec)
perf2 <- performance(pred2, "tpr", "fpr")
pred3 <- prediction(Avec.pred3, Avec)
perf3 <- performance(pred3, "tpr", "fpr")
# get AUC
aucs <- c()
for (v in c(pred1, pred2, pred3)) {
    auc <- performance(v, "auc")
    v <- slot(auc, "y.values")[[1]]
    aucs <- c(aucs, v)
}

```

Summarizing the results from the eigenmodels, using the original combined network adjacency matrix as a reference, we estimated the *Area Under the Curve* (AUC) statistics for each model.
Compared to the latent model ($\ AUC_{latent}$ =`r round(aucs[1], 3)`), the inclusion of the tool-level grouping factor resulted in a better predictive model ($\ AUC_{latent+tool}$ = `r round(aucs[2], 3)`).
The final model involving the scale-level vertex characteristics has the best goodness-of-fit ($\ AUC_{latent+scale}$ =`r round(aucs[3],3)`).
See Figure 4. in the Appendix for the corresponding ROC curves.

### 3.6 Network accuracy and stability

We used the *bootnet* R package to have an estimate of edge-weight accuracy with *non-parametric bootstrap* (2500 times sampling).
The resulting **accuracy** estimates have been visually incorporated in Figure 1 in the following manner.
Edge shade reflects the lower bound of the 95% confidence interval (CI) for each edge, while edges are presented with dashed line for cases of the CI including 0.0 edge weights.
For such cases,  we cannot be sure if their weight persist given different samples and varying sample characteristics.
Darker shaded, continuous edges are stable according to this bootstrap estimate and they preserve their sampled nature.
Cases like the relatively strong edge between *SCRS(5)* and *SCRS(7)* items indicate moderate penalized partial correlation between items in the SCRS network ($\rho$=`r round(E(SCRS_graph)[attributes(E(SCRS_graph))[1][[1]]=='SCRS_5|SCRS_7']$strength,3)`), but the edge is presented with dashed line and has lighter shade indicating a lower stability. 
Such edges are less likely to exhibit similar characteristics with varying samples.

Network **stability** estimates for our three networks were carried out by using the *bootnet* function from the R package bearing the same name. 
We performed a *case dropping bootstrap* to simulate scenarios where fewer and fewer cases of the original sample would have been available and quantified the stability of the centrality metrics with the *Correlation Stability* (CS) coefficient. 
Bootstrap was performed with B=2500 resamples.


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

RRS_stability <- readRDS("output/RRS_stability.RDS")
SCRS_stability <- readRDS("output/SCRS_stability.RDS")
combined_stability <- readRDS("output/combined_stability.RDS")

# edge_summary(rumi, accuracy_combined, combined_stability)
# edge_summary(RRS_graph, accuracy_rrs, RRS_stability)
# edge_summary(accuracy_scrs, SCRS_stability)
```

\newpage
\blandscape

## Appendix

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(summary_table, format='simple', row.names=FALSE,caption="Network descriptive statistics for RRS, SCRS and their combined networks",label='Table 1',digits=2)
```

*Deg.=Degree; Str.=Strength; Bet.=Betweenness; Clo.=Closeness; EI1= One-step Expected Influence; EI2= Two-step Expected Influence; Br.Str.=Bridge Strenth; Br.Bet.=Brdige Betweenness; Br.Cl.=Bridge Closeness; Br.EI1=One-step Bridge Expected Influence; Br.EI2=Two-step Bridge Expected Influence; TPR=average True Positive Rate*

\elandscape

\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(RRS_graph, accuracy_rrs,RRS_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the RRS network",label='Table 2',digits=2)
```

*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Accuracy by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*

\elandscape
\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(SCRS_graph, accuracy_scrs,SCRS_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the SCRS network",label='Table 2',digits=2)
```


*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Accuracy by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*

\elandscape
\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(rumi, accuracy_combined,combined_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the RRS and SCRS network",label='Table 2',digits=2)
```

*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Accuracy by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*


\elandscape
\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE,fig.retina=1,fig.align='center', fig.width=16, fig.height=10, fig.cap='ROC curves of the combined RRS-SCRS network'}

ROC_data <- bind_rows(getAUC(perf1, "Latent effect"), getAUC(perf2, "Latent + Tool as pair-wise"), getAUC(perf3, "Latent + Scale as pair-wise"))

aucs_labels <- ""
conds <- c("Latent effect", "Latent + Tool", "Latent + Scale")
cond_lab <- ""

for (i in seq_along(conds)) {
    cond_lab <- paste0(cond_lab, conds[i], ":\n")
}

for (i in seq_along(conds)) {
    aucs_labels <- paste0(aucs_labels, round(aucs[i], 3), "\n")
}


ggplot(ROC_data, aes(x, y)) +
    geom_path(aes(x, y, group = Condition, color = Condition, linetype = Condition), size = 0.75) +
    scale_color_manual(values = c("gray69", "black", "gray50")) +
    theme_bw() +
    labs(x = "False Positive Rate", y = "True Positive Rate") +
    geom_rect(aes(xmin = 0.75, ymin = 0, xmax = 1.0, ymax = 0.25), fill = "white", color = "gray70") +
    geom_text(x = 0.8, y = 0.23, label = "AUC:") +
    geom_text(x = 0.82, y = 0.1, label = cond_lab) +
    geom_text(x = 0.92, y = 0.1, label = aucs_labels) +
    theme(legend.position = "bottom")
```

## References
