---
title: "Self-critical rumination - A network approach"
bibliography: rumination.bibtex
csl: apa7.csl
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# libraries declared
library(tidyverse)
library(networktools)
library(qgraph)
library(glasso)
library(ggraph)
library(igraph)
library(bootnet)
library(modelr)
library(scales)
library(knitr)
source("R/data_import.R")
source("R/functions.R")
# data import
source("../networks_with_r/get_rumi.R")
setwd('/home/tamas/repos/rumination_lasso')
```

## 2. Methods

### 2.1 Network analysis
*Psychological networks* have their own characteristics which differentiate them from other networks of the graph theory [@Epskamp2017; @Newman2010]. 
Nodes usually represent some psychological measures or items of a psychological assessment tool, while the edges of the network reflect the corresponding estimates of association derived from the data.
Having two rumination-related questionnaires, we assumed

* network analysis will reveal their respective internal structure previously established in the literature (RRS having a two-scale structure: reflection and brooding; while SCRS will show a single-scale structure);
* on the other hand, we hypothesized that in their common network, items overlapping in scope will change these clear outlines of the two measurement tools. According to our hypothesis, items of the RRS scale 'brooding' will have non-trivial association with the self-critical aspects of rumination;
* thus, we also assumed a combined rumination network, representing the generic (more trait-like) and the self-critical aspects of rumination will exhibit a three-component structure.

<!-- Sample sizes have direct impact on estimated accuracy and stability of the psychological network, thus the accuracy of the network parameters and measures is crucial: By obtaining robust results we can have a more realistic picture of a network without knowing the true network shape and structure. --> 
<!-- Just like any other psychological variables, network characteristics are also sensitive to sampling, estimation methods, included variables, outliers and various other components of an analysis. --> 
<!-- As [@Epskamp2017a] points out, psychological networks differ from *reflective latent variable models* by not seeking for a common cause of co-occurrence of variables (such as symptoms or different items of a questionnaire), but instead their focus is on quantifying and visually show the multivariate dependencies and the different pathways of direct relationships between the nodes. --> 
<!-- A major conceptual difference emerges from the network perspective for psychological data: psychological variables, such as symptoms, states, attitudes and other constructs (represented as nodes) have direct impact on each other, and are not caused by some latent variables.  [@Epskamp_2018]. --> 
In the current study, we used a fairly large sample of indiviuals (N=`r nrow(rumi_data)`) to construct a dense, undirected network of rumination-related psychological constructs. 
The vertices represent the items of the Ruminative Response Style (RRS) and the Self-critical Rumination Scale (SCRS), while edges are penalized partial correlations (using LASSO penalization, [@Friedman2007] ).


#### 2.1.1 Least Absolute Shrinkage and Selection Operator (LASSO)

We constructed individual and combined networks of RRS and SCRS with respective penalized correlation matrices using the *EBICglasso* function of the **qgraph** package (number of lambda parameters were set to 1000).
In order to shrink the edges, achieve high specificity, and get a less dense network, we let the function to exclude any elements of the underlying precision matrix below a threshold value (*threshold* parameter set to TRUE).

The LASSO uses L1 regularization([@Tibshirani1996], [@Friedman2007]), and in the current study, it results in a partial correlation network where edges represent direct associations between pairs of items, while the influence of all other items in the network are kept controlled. 
The regularization by L1 penalty ensures that trivially small partial correlations are set to zero [@McNally_2017], thus ensure a *sparse* network which are more interpretable (@Epskamp_2018). 

The tuning parameter of *gamma* in the graphical LASSO algorithm has been set to 0.5 value in accordance with [@McNally_2017] and [@Bernstein2019] in order to achieve sparse graphs. 
The final networks were chosen by the lowest values of the *extended Bayesian Information Criterion* (EBIC).

<!-- Before going further into network modeling, we estimated the 95% confidence intervals of network centrality measures to have an understanding of the sampling distribution of our estimates. According to @Epskamp2017a low sample size and non-regularized estimates might lead to amplify any bootstrap bias; by having a larger sample of individuals, we expect lesser levels of bias of any bootstrap estimates for network accuracy and stability. -->

#### 2.1.2 Goldbricker

We applied the *goldbricker* function from the R package *networktools* [@Jones2017] in order to search for pairs of items in the RRS, SCRS and their combined networks that were highly correlated (r > 0.75) and exhibited the same pattern with other items. 


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dataset <- rumi_data
var_names <- names(dataset)
```
After the LASSO regularization no further dimensionality reduction was necessary based upon the *goldbricker* evaluation.
As subject for this paper,


#### 2.1.3 Network descriptives
A comparative overview of the three networks were produced with their descriptives (degree distribution) and their centrality measures (strength, closeness, betweenness; [@GaborCsardi2020]), their One- and Two-Step Expected Influence (EI) measures ([@Robinaugh2016], [@Heeren2018]).
In order to further elaborate the question of vertex importance, we identified *bridge nodes* using the functions provided by the *networktools* R package [@Jones2017]. 
We estimated both one-step and two-step bridge expected influence measures which reflect the sum of edge weights connecting one vertex to other groups on vertices (or communities); and also express a vertex's secondary influence on the rest of the network, respectively. 
Higher influence scores indicate that a certain node is more likely to active neighbouring nodes, subgroups of nodes or communities.

#### 2.1.3. Community detection
In order to get an understanding of community of nodes and to see if nodes can be grouped into neighbourhoods, we used the *igraph* R package. When detecting possible communities of nodes, the detection happened with the following parameters in the *spin glass algorithm* [@Reichardt2006; @Bernstein2019].

#### 2.1.6. Network accuracy and stability
Accuracy and stability have an important role in estimating network parameters when samples might vary in characteristics and size [@Epskamp2017; @Epskamp2017a]. One way of estimating network accuracy is to produce a 95% confidence interval of edge-weights with some variant of bootstrap. In our case we chose the non-parametric variant because of interpretability. Network stability is quantified with the *Correlation Stability* (CS-coefficient): an estimate of the maximum proportion of cases that can be dropped (with 95% certainty) to retain a correlation with the original centrality of higher than 0.7. Simulation studies [@Epskamp2017] show that the CS-coefficient should be between 0.25 and 0.5. 


 
## 3. Results

## 3.1.1. Network descriptives

The RRS (order of `r vcount(RRS_graph)`, size of `r ecount(RRS_graph)`) and SCRS (order of `r vcount(SCRS_graph)`, size of `r ecount(SCRS_graph)`) networks are densely connected relational networks.
While SCRS exhibits no *articulation point* (also call *cut vertex* whose removal would disconnect the network [@GaborCsardi2020]), the vertex of the *'problem'* item of RRS acts as an articulation point, as it would cut off the *'deserve'* vertex.
The RRS internal structure 
The combined network (order: `r vcount(rumi)`, size: `r ecount(rumi)`) has no articulation points, 


```{r }
# simulate_communities(RRS_graph, path="output/RRS_communities.RDS",i=1000)
# simulate_communities(SCRS_graph, path="output/SCRS_communities.RDS",i=1000)
# simulate_communities(rumi, path="output/combined_communities.RDS",i=1000)
RRS_simulated_communities <- readRDS("output/RRS_communities.RDS")
SCRS_simulated_communities <- readRDS("output/SCRS_communities.RDS")
combined_simulated_communities <- readRDS("output/combined_communities.RDS")

RRS_simulated_communities  %>%
    group_by(Item, Community)  %>%
    summarize(N= n())
SCRS_simulated_communities  %>%
    group_by(Item, Community)  %>%
    summarize(N= n())
combined_simulated_communities  %>%
    group_by(Item, Community)  %>%
    summarize(N= n())

simulate_communities(SCRS_graph, path="output/SCRS_communities.RDS")
summary_table <- bind_rows(network_summary(RRS_graph, name="RRS",seed=seed,method=method,weights=weights),
                            network_summary(SCRS_graph, name="SCRS", seed=seed,method=method,weights=weights),
                            network_summary(rumi, name="Combined RRS+SCRS",seed=seed,method=method,weights=weights))

knitr::kable(summary_table, format='simple', row.names=FALSE,label="Network descriptive statistics for RRS, SCRS and their combined networks")

```

### 3.1 Network plots
When estimating networks, we modeled RRS, SCRS and their combined network as Gaussian graph-networks which are networks of partial correlation coefficients [@Epskamp2018]. In many parts of this analysis we also utilized functions from the *qgaph* R package [@Epskamp2012]. Please refer Fig. 1-3.



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "RRS network with gLASSO"}

RRS_labels <- data_labels[grep("RRS", data_labels$var),]$labels
RRS_labels  <- RRS_labels[1:(length(RRS_labels)-3)]
RSScov2 <- qgraph::cor_auto(RRS_subset)
rss_network <- qgraph(RSScov2, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 888, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = RRS_labels)

#rss_network  <- estimateNetwork(RRS_subset, default="EBICglasso")
```



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "SCRS network with gLASSO"}

SCRS_labels <- data_labels[grep("SCRS", data_labels$var),]$labels
SCRScov <- qgraph::cor_auto(SCRS_subset_reduced)
scrs_network <- qgraph(SCRScov, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 888, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = SCRS_labels)

#scrs_network  <- estimateNetwork(SCRS_subset, default="EBICglasso")
```




```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Combined RRS and SCRS network"}

# full data scenario
# MHC not included!
full_data <- dataset[, c(RRS_items, SCRS_items)] 
full_goldbricker <- goldbricker(full_data, p = 0.05, method = "hittner2003", threshold = 0.25, corMin = 0.5, progressbar = TRUE)
saveRDS(full_goldbricker, "output/full_goldbricker.RDS")
full_goldbricker <- readRDS("output/full_goldbricker.RDS")


#full_goldbricker$suggested_reductions
full_reduced <- net_reduce(full_data, full_goldbricker, method = c("PCA", "best_goldbricker"))
full_cov <- qgraph::cor_auto(full_reduced)
full_labels  <- c(RRS_labels, SCRS_labels)
full_network <- qgraph(full_cov, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 888, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = full_labels)

```

### 3.2 Community detection 
Community mapping of RSS and SCRS with the *spin glass algorithm* [@Reichardt2006; @Bernstein2019].


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "RSS communities identified with parameters *gamma = 0.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*"}

make_community_graph(rss_network, RSScov2, RRS_labels)
```

RRS items (Fig.4.) are grouped into two communities. In one we find the strongly connected items *alone1* and *alone2* with items *write*, *person* and *analyze*. The rest of the items constitute the other main community.




```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "SCRS communities identified with parameters *gamma = 0.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*."}

make_community_graph(scrs_network, SCRScov, SCRS_labels)
```

The self-critical rumination items exhibit one large community as a whole (Fig.5.).



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap ="RRS and SCRS combined communities identified with parameters *gamma = -1.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*."}

make_community_graph(full_network, full_cov, full_labels)

```

When all RRS and SCRS items are handled as one covariance and one Gaussian graph-network, 4 items of RRS (*handle*, *problem*, *deserve* and *wish*) are grouped into the community of the SCRS items (Fig.6.).



### 3.3 Expected Influence
In order to estimate the Expected Influence metrics, we used the *expectedInf* function of the *networktools* R package. The influence score are standardized.




```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, fig.cap= "RRS Expected Influence Measures"}
expected_inf_plot(rss_network, "RRS")
```

Regarding RRS influence estimates (Fig.7.): Items such as *alone1*, *alone2* and *person* are high in terms of expected influence, meaning that these items play more central role in the RRS network, by changing these nodes, the rest of the network changes more likely.




```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, fig.cap = "SCRS Expected Influence Measures"}
expected_inf_plot(scrs_network, "SCRS")
```

SCRS-items (Fig.8.) such as *habits* and *thoughts* are more influencing nodes than *productive*.


```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, fig.cap = "Combined RRS and SCRS Expected Influence Measures"}
expected_inf_plot(full_network, "RRS & SCRS")
```

In the combined network scenario (Fig.9.), the RRS item *alone1*, the SCRS items *habits* and *thoughts* maintain their influencing position among the items. Due to the combination of tools, the SCRS item *different* has increased its influence, and the items *mistakes and aspects* have increased their impact as a PCA component. This also means that in the combined network they proved to be too redundant and the *goldbricker* algorithm used their PCA-component instead.


### 3.4 Bridge nodes

Using the *networktools* R library bridge expected influence measure were estimated for the three tools we used in this study. We also added aesthetics to reflect which items belonged to the same community according to our previous clustering steps (Fig. 10-12.).




```{r echo=FALSE, fig.height=4, fig.width=11, message=FALSE, warning=FALSE, fig.cap = "RRS bridge estimates"}
# get the estimate of bridge influence scores
make_bridge_plot(rss_network, "RRS")
```



```{r echo=FALSE, fig.height=4, fig.width=11, message=FALSE, warning=FALSE, fig.cap = "SCRS bridge estimates"}
make_bridge_plot(scrs_network, "SCRS")
```


```{r echo=FALSE, fig.height=4, fig.width=11, message=FALSE, warning=FALSE, fig.cap = "Combined RRS and SCRS bridge estimates"}
# make_bridge_plot(full_network, "RSS & SCRS")
```




### 3.5 Network accuracy and stability
We used the *bootnet* R package to have an estimate of edge-weight accuracy with *non-parametric bootstrap* (2500 times sampling) and also produce measures of centrality stability with *case dropping bootstrap* (to simulate cases where only the subset of the existing data would be available).

Network accuracy plots show pairs of nodes (pairs of items) by ascending order of the edge-weights. 95% confidence intervals and the vertical line of 0 edge-weight are shown separately.



```{r echo=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE, fig.cap = "Network accuracy estimate for RRS"}
# generate the accuracy estimate and save it
#RRS_network <- estimateNetwork(RRS_subset, default="EBICglasso")
#accuracy_rrs  <- bootnet(RRS_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_rrs, "../output/accuracy_rrs.RDS")

accuracy_rrs  <- readRDS("output/accuracy_rrs.RDS")
network_accuracy_plot(accuracy_rrs, "RRS")
```
From the pair of items *react* and *alone1* confidence intervals of edge weights start to incorporate the value of 0 and thus we cannot be sure if their weight persist given different samples and varying sample characteristics.




```{r echo=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE, fig.cap = "Network accuracy estimate for SCRS"}
# generate the accuracy estimate and save it
#SCRS_network <- estimateNetwork(SCRS_subset, default="EBICglasso")
#accuracy_scrs  <- bootnet(SCRS_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_scrs, "../output/accuracy_scrs.RDS")

accuracy_scrs  <- readRDS("output/accuracy_scrs.RDS")
network_accuracy_plot(accuracy_scrs, "SCRS")
```
Similar to RRS, SCRS item pairs are ordered by their edge-weight estimates. Below the pair of items of *time* and *mistake*, accuracy might not be non-zero under different sampling conditions.
The combined RRS and SCRS network estimates are added to the *Appendix* section of this paper.


Network stability estimates for our three networks were carried out by using the *bootnet* function from the R package bearing the same name. We performed a *case dropping bootstrap* to simulate scenarios where fewer and fewer cases of the original sample would have been available and quantified the stability of the centrality metrics with the *Correlation Stability* (CS) coefficient. When estimating bootstrap, we set the number of bootstraps to 2500.



```{r echo=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, fig.cap = "Stability estimates of the RRS network centrality indices"}

#RRS_network <- estimateNetwork(RRS_subset, default="EBICglasso")
#RRS_stability <- bootnet(RRS_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(RRS_stability, "../output/RRS_stability.RDS")

#SCRS_network <- estimateNetwork(SCRS_subset, default="EBICglasso")
#SCRS_stability <- bootnet(SCRS_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(SCRS_stability, "../output/SCRS_stability.RDS")

#full_network <- estimateNetwork(full_data, default="EBICglasso")
#full_stability <- bootnet(full_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(full_stability, "../output/full_stability.RDS")




plot_RRS_stab <- readRDS("output/plot_RRS_stability.RDS")
network_stability_plot(plot_RRS_stab)
```
Edge weights and node strength estimates exhibit strong stability, whereas closeness estimates are more sensitive to sample size drops. Betweenness scores seem to be insensitive to sample sizes and are consistently weak in terms of their low correlations with the original estimates for RRS.





```{r echo=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, fig.cap="Stability estimates of the SCRS network centrality indices"}
plot_SCRS_stab <- readRDS("output/plot_SCRS_stability.RDS")
network_stability_plot(plot_SCRS_stab)
```
Edge weights, node strength and closeness estimates exhibit strong stability,while betweenness scores seem to be insensitive to sample sizes and are consistently weak in terms of their low correlations with the original estimates for SCRS, similar to RRS.

```{r echo=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
#stability
RRS_stability <- readRDS("output/RRS_stability.RDS")
SCRS_stability <- readRDS("output/SCRS_stability.RDS")
full_stability <- readRDS("output/full_stability.RDS")



#CS estimates

#RRScorStab <-corStability(RRS_stability)
#saveRDS(RRScorStab, "../output/RRScorStab.RDS")
#SCRScorStab <- corStability(SCRS_stability)
#saveRDS(SCRScorStab, "../output/SCRScorStab.RDS")
#fullcorStab <- corStability(full_stability)
#saveRDS(fullcorStab, "../output/fullcorStab.RDS")

RRScorStab <- readRDS("output/RRScorStab.RDS")
SCRScorStab <- readRDS("output/SCRScorStab.RDS")
fullcorStab <- readRDS("output/fullcorStab.RDS")

CS_estimates <- tibble(RRS = RRScorStab,
       SCRS = SCRScorStab,
       combined = fullcorStab)

rownames(CS_estimates) <- names(RRScorStab)

CS_estimates <- CS_estimates %>% 
  mutate(measure = rownames(CS_estimates)) %>% 
  select(Metric = measure, RRS, SCRS, combined)
knitr::kable(CS_estimates, 
             caption = "Correlation Stability coefficient estimates for RRS, SCRS and their combined network", digits = 4)
```

As shown at [@Epskamp2017], the CS-coefficent is ideally between 0.25 and 0.5, the latter is the cat-off point for the estimate. The results show that RRS and SCRS closeness metrics are stable in the sense that around 28% of the case can be dropped to still maintain 0.7 or higher correlation with their original estimates. The closeness measure (`r round(CS_estimates[2, 4][[1]],4)`) for their combined network is already higher than the 0.5 cut-off. The same applies to all edge and strength estimates, with no regard of the network of RRS, SCRS or their combined variant. Betweenness measures are too low to be considered secure to interpret (all below 0.25) meaning that even slight case drops result in losing their stability.


## 4. Discussion
As [@Jones2018] pointed out, when network modeling is done by using force-directed networks[Fruchterman hivatkozas!!!], node placement is not directly interpretable, as these graph are rendered to be aesthetic. 

## Appendix



```{r echo=FALSE, fig.height=20, fig.width=14, message=FALSE, warning=FALSE, fig.cap="Network accuracy estimate for combined RRS and SCRS"}
# generate the accuracy estimate and save it
#combined_network <- estimateNetwork(full_data, default="EBICglasso")
#accuracy_combined  <- bootnet(combined_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_combined, "../output/accuracy_combined.RDS")

accuracy_combined  <- readRDS("output/accuracy_combined.RDS")
# network_accuracy_plot(accuracy_combined, "combined RRS and SCRS", save_data=TRUE)
```

This combined accuracy estimates for RRS and SCRS include pairs of items from both questionnaires. The last pair of items where the confidence interval does not include 0 edge-weight is the pair of *handle* from RRS and *mistakes* from SCRS. The majority of the more accurate pair estimates are homogeneous in the sense that they are not RRS-SCRS mixed pairs (they are both either from RRS or SCRS). *Handle* belonged to the community of the SCRS nodes in our community analysis.


## References
