---
title: "Self-critical rumination - A network approach"
bibliography: rumination.bibtex.bib
csl: apa7.csl
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

output:
  bookdown::pdf_document2

---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# libraries declared
library(tidyverse)
library(networktools)
library(qgraph)
library(glasso)
library(ggraph)
library(igraph)
library(bootnet)
library(modelr)
library(scales)
library(knitr)
library(ggpubr)
library(broom)
library(ergm)
library(fdrtool)
library(eigenmodel)
library(ROCR)
library(bookdown)
source("R/data_import.R")
source("R/functions.R")
# data import
source("../networks_with_r/get_rumi.R")
suppressMessages(extrafont::loadfonts(device='postscript'))
setwd('../networks_with_r')
source("get_rumi.R")
source("src/functions.R")
setwd('/home/tamas/repos/rumination_lasso')
```

## 2. Methods

### Hypothesis and the use of Network Analysis
*Psychological networks* have their own characteristics which differentiate them from other networks of the graph theory (@Epskamp2017; @Epskamp_2018; @Newman2010). 
Vertices (also called nodes) usually represent some psychological measures or items of a psychological assessment tool, while the edges of the network reflect the corresponding estimates of association derived from the data.
Having two rumination-related questionnaires, we assumed the following hypotheses:

* Network analysis will reveal their respective internal structure previously established in the literature (sich as *RRS* having a two-scale structure: *reflection* and *brooding*; while *SCRS* will show a single-scale structure);
* on the other hand, we hypothesized that in their common network, items overlapping in scope will change these clear outlines of the two measurement tools. According to our hypothesis, items of the *RRS* scale 'brooding' will have non-trivial association with the self-critical aspects of rumination;
* thus, we also assumed a combined rumination network, representing the generic (more trait-like) and the self-critical aspects of rumination will exhibit a three-component structure.

<!-- Sample sizes have direct impact on estimated accuracy and stability of the psychological network, thus the accuracy of the network parameters and measures is crucial: By obtaining robust results we can have a more realistic picture of a network without knowing the true network shape and structure. --> 
<!-- Just like any other psychological variables, network characteristics are also sensitive to sampling, estimation methods, included variables, outliers and various other components of an analysis. --> 
<!-- As [@Epskamp2017a] points out, psychological networks differ from *reflective latent variable models* by not seeking for a common cause of co-occurrence of variables (such as symptoms or different items of a questionnaire), but instead their focus is on quantifying and visually show the multivariate dependencies and the different pathways of direct relationships between the nodes. --> 
<!-- A major conceptual difference emerges from the network perspective for psychological data: psychological variables, such as symptoms, states, attitudes and other constructs (represented as nodes) have direct impact on each other, and are not caused by some latent variables.  [@Epskamp_2018]. --> 
In the current study, we used a fairly large sample of indiviuals (N=`r nrow(rumi_data)`) to construct a dense, undirected network of rumination-related psychological constructs. 
The vertices represent the items of the **Ruminative Response Style **(*RRS*) and the **Self-critical Rumination Scale** (*SCRS*), while edges are penalized partial correlations (using LASSO penalization, see @Friedman2007; @Tibshirani1996).


### 2.1. Least Absolute Shrinkage and Selection Operator (LASSO)

We constructed individual and combined networks of *RRS* and *SCRS* with respective penalized correlation matrices using the *EBICglasso* function of the **qgraph** package (@Epskamp2012a; see our Git repository for other parameter specifications).
In order to shrink the edges, achieve high specificity, and get a less dense network, we let the function to exclude any elements of the underlying precision matrix below a threshold value (*threshold* parameter set to TRUE).

The LASSO uses *L1* (absolute) regularization(@Tibshirani1996, @Friedman2007), and in the current study, it results in a partial correlation network where edges represent direct associations between pairs of items, while the influence of all other items in the network are kept controlled. 
The regularization by L1 penalty ensures that trivially small partial correlations are set to zero (@McNally_2017), thus ensure a *sparse* network which are more interpretable (@Epskamp_2018). 

The tuning parameter of *gamma* in the graphical LASSO algorithm has been set to 0.5 value in accordance with [@McNally_2017] and [@Bernstein2019] in order to achieve sparse graphs. 
The final networks were chosen by the lowest values of the *extended Bayesian Information Criterion* (EBIC).

<!-- Before going further into network modeling, we estimated the 95% confidence intervals of network centrality measures to have an understanding of the sampling distribution of our estimates. According to @Epskamp2017a low sample size and non-regularized estimates might lead to amplify any bootstrap bias; by having a larger sample of individuals, we expect lesser levels of bias of any bootstrap estimates for network accuracy and stability. -->

### 2.2 Redundant items

We applied the *goldbricker* function from the R package *networktools* [@Jones2017] in order to search for pairs of items in the *RRS*, *SCRS* and their combined networks that were highly correlated (r > 0.75) and exhibited the same pattern with other items. 


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dataset <- rumi_data
var_names <- names(dataset)
```
After the LASSO regularization no further dimensionality reduction was necessary based upon the *goldbricker* evaluation.


### 2.3 Network descriptives

A comparative overview of the three networks was produced with their descriptives (degree distribution) and their centrality measures (strength, closeness, betweenness; @GaborCsardi2020), and their One- and Two-Step Expected Influence (EI) measures to understand the cumulative importance of vertices (@Robinaugh2016, @Heeren2018, @Bernstein2019).
In order to further elaborate the question of vertex importance, we identified *bridge nodes* using the functions provided by the *networktools* R package (@Jones2017) to identify bridge vertices (connectors between sub-graphs, see and example at @Bernstein2019). 
We estimated both one-step and two-step bridge expected influence measures which reflect the sum of edge weights connecting one vertex to other groups on vertices (or communities); and also express a vertex's secondary influence on the rest of the network, respectively. 
Higher influence scores indicate that a certain node is more likely to active neighbouring nodes, subgroups of nodes or communities.
In order to estimate the Expected Influence metrics, we used the *expectedInf* function of the *networktools* R package.
Using the *networktools* R library, bridge expected influence measure were also estimated for the two questionnaires we used in this study.

### 2.4. Community detection
In order to get an understanding of community of vertices and to see if vertices can be grouped into neighbourhoods corresponding to the previously established sub-scale structure of *RRS*, *SCRS* and investigate their separation in their combined network, we used the community detection methods of the *igraph* R package (@GaborCsardi2020). 
When detecting possible communities of vertices, we followed guidlines by @Reichardt2006, @Bernstein2019 and @GaborCsardi2020.
In order to mitigate the effect of choice of community detection algorithms we performed more of them available in the *igraph* package multiple times.

### 2.5. Network accuracy and stability
Accuracy and stability have an important role in estimating network parameters when samples might vary in characteristics and size [@Epskamp2017; @Epskamp2017a]. 
One way of estimating network accuracy is to produce a 95% confidence interval of edge-weights with some variant of bootstrap. 
In our case we chose the non-parametric bootstrap estimate for sake of interpretability, where the penalized partial correlation coefficients formed the edge weights. 
Network stability is quantified with the *Correlation Stability* (CS-coefficient): an estimate of the maximum proportion of cases that can be dropped (with 95% certainty) to retain a correlation with the original centrality higher than some fixed threshold value (in the present paper, 0.7). 
Simulation studies [@Epskamp2017] lead us in our expectation as the CS-coefficient should be between 0.25 and 0.5. 


 
## 3. Results

### 3.1 Network descriptives

The undirected, weighted, associational networks of *RRS*, *SCRS* and their combined structure can be seen below (see Figure 1).
All three networks proved to be connected (any vertex is reachable from every other).
Comparing diameters to mean distances, we see densely connected graphs (for the *RRS* network, its diameter is `r round(diameter(RRS_graph),3)` compared to its mean distance of `r round(mean_distance(RRS_graph),3)`; the *SCRS* and the combined networks show similar patterns; see Figure 1.).
On the plot, vertices represent the corresponding items of each questionnaire with labels showing item number, sub-scale and a label for each item.
Sub-scales are presented in a colour-coded fashion as the outer circle of each vertex.
Edges are the **LASSO** *L1*-penalized partial correlation coefficients whose value is represented as shade and width of the arcs.

The *RRS* (order of `r vcount(RRS_graph)`, size of `r ecount(RRS_graph)`) and *SCRS* (order of `r vcount(SCRS_graph)`, size of `r ecount(SCRS_graph)`) networks are densely connected networks.
While *SCRS* exhibits no *articulation point* (also called *cut vertex* whose removal would disconnect the network; @GaborCsardi2020), the vertex of the *'problem'* (*"What am I doing to deserve this?"*) item of *RRS* acts as an **articulation point**, as it would cut off the *'deserve'* (*"Why do I have problems other people don't have?"*) vertex.
Articulation points are marked with * on Figure 1.
Besides **size** and **order**, on Figure 1. we also indicated the **Clustering coeffient** (*transitivity*), the **diameter** and the average vertex-to-vertex path lengths (**mean distance**).

The combined network (order: `r vcount(rumi)`, size: `r ecount(rumi)`) has no articulation points.
The previously identified articulation point of the *RRS* network (*problem* vertex) is no longer a cut-off edge.

In order to analyze their respective internal structures, we performed community detection using the *igraph* package in R.
On Figure 1., the inner node point of each vertex provides colour coding for our community detection results (the presented shades correspond to the True Positive Rates of each sub-scale; in other words, the average match between the detected community and the original sub-scale).


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
i  <- 1000
# simulate_communities(RRS_graph, path="output/RRS_communities.RDS",i=i)
# simulate_communities(SCRS_graph, path="output/SCRS_communities.RDS",i=i)
# simulate_communities(rumi, path="output/combined_communities.RDS",i=i)
RRS_simulated_communities <- readRDS("output/RRS_communities.RDS")
SCRS_simulated_communities <- readRDS("output/SCRS_communities.RDS")
combined_simulated_communities <- readRDS("output/combined_communities.RDS")

# RRS_item_TPR <- item_level_TPR(RRS_simulated_communities, RRS_graph, threshold=0.95)
# saveRDS(RRS_item_TPR, 'output/RRS_item_TPR.RDS')
# SCRS_item_TPR <- item_level_TPR(SCRS_simulated_communities, SCRS_graph, threshold=0.5)
# saveRDS(SCRS_item_TPR, 'output/SCRS_item_TPR.RDS')
# combined_item_TPR <- item_level_TPR(combined_simulated_communities, rumi)
# saveRDS(combined_item_TPR, 'output/combined_item_TPR.RDS')
RRS_item_TDR <- readRDS('output/RRS_item_TPR.RDS')
SCRS_item_TDR <- readRDS('output/SCRS_item_TPR.RDS')
combined_item_TDR <- readRDS('output/combined_item_TPR.RDS')
accuracy_rrs  <- readRDS("output/accuracy_rrs.RDS")
accuracy_scrs  <- readRDS("output/accuracy_scrs.RDS")
accuracy_combined <- readRDS("output/accuracy_combined.RDS")
accuracy_rrs <- network_accuracy_data(accuracy_rrs)
accuracy_scrs <- network_accuracy_data(accuracy_scrs)
accuracy_combined <- network_accuracy_data(accuracy_combined)

get_itemnames <- function(namevector){
    grid <- tibble(expand.grid(namevector, namevector))
    grid <- grid %>% filter(!Var1==Var2)
    grid


}
# add accuracy to networks
rumi <- add_accuracy_to_graph(rumi, accuracy_combined)
RRS_graph <- add_accuracy_to_graph(RRS_graph, accuracy_rrs)
SCRS_graph <- add_accuracy_to_graph(SCRS_graph, accuracy_scrs)

overalltextsize <- 24
textsize=5
RRS_plot <- beautify(RRS_graph, RRS_simulated_communities, title="RRS undirected graph", no_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize,item_TDR=RRS_item_TDR)
SCRS_plot <- beautify(SCRS_graph, SCRS_simulated_communities, title="SCRS undirected graph", no_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize,item_TDR=SCRS_item_TDR)
combined_plot <- beautify(rumi, combined_simulated_communities, title="RRS & SCRS undirected graph",force_caption=TRUE, textsize=textsize, overalltextsize=overalltextsize, item_TDR=combined_item_TDR)
network_plot <- ggarrange(ggarrange(RRS_plot, SCRS_plot, nrow=2,heights=c(1,1)), combined_plot, widths=c(0.95,1.05))
# ggsave("output/networkplot.png",network_plot, dpi=400, device='png',width=27, height=14)

# RRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# SCRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# combined_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
RRS_tpr <- suppressMessages(get_TPR(RRS_simulated_communities,RRS_graph))

RRS_tpr_s <- suppressMessages(RRS_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

SCRS_tpr <- suppressMessages(get_TPR(SCRS_simulated_communities,SCRS_graph))
SCRS_tpr_s <- suppressMessages(SCRS_tpr %>% 
    group_by(Subscale, Method, Weights)  %>%
    summarise(TPR_m = mean(TPR)))

combined_tpr <- suppressMessages(get_TPR(combined_simulated_communities,rumi))
combined_tpr_s <- suppressMessages(combined_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

combined_tpr_top <- suppressMessages(combined_tpr %>% 
    filter(!Method %in% c("walktrap", "optimal","fast_greedy")) %>%
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))



# summary table 
seed <- 647
weights <- TRUE
method <- 'optimal'
summary_table <- bind_rows(network_summary(RRS_graph, name="RRS",seed=seed,method=method,weights=weights, item_TPR=RRS_item_TDR),
                            network_summary(SCRS_graph, name="SCRS", seed=seed,method=method,weights=weights, item_TPR=SCRS_item_TDR),
                            network_summary(rumi, name="Combined",seed=seed,method=method,weights=weights, item_TPR=combined_item_TDR))

```

\newpage
\blandscape

```{r networkPlot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE,fig.retina=1,fig.align='center', fig.width=32, fig.height=20, fig.cap='Tableau view of three graphs of rumination'}
network_plot
```

\elandscape

As the choice of algorithm has non-trivial impact on the identified community structure, after having selected the *"optimal"*, the *"spinglass"*, the *"walktrap"* and (to also include hierarchical clustering) the *"fast greedy"* methods, we tested each a `r i` times on the three networks.
We also provided an edge weight vector in the form of the *LASSO*-penalized partial correlation coefficients (or alternatively, omitted weights).

The **RRS** two-scale structure could be recreated with all four algorithms with the inclusion of the weight vector not having effect on the measures.
For the sub-scale of *brooding* the average **true positive rate** (TPR) was `r RRS_tpr_s[1,2][[1]]`; for *reflection*  `r round(RRS_tpr_s[2,2][[1]],3)`.
In case of the *reflection* sub-scale, lower average TPR becomes tangible with the inspection of items 2 (*"analyze"*; *"Analyze recent events to try to understand why you are depressed"*) and 9 (*"person"*; *"Analyze your personality to try to understand why you are depressed"*) whose low TPR indicates that depending in the choice of community detection they have a chance of forming their own community or being classified as members of the *brooding* scale, rather than being part of 'reflection'.


In the case of *SCRS*, the best TPR of `r SCRS_tpr_s[7,4][[1]]` has been achieved with `r SCRS_tpr_s[7,2][[1]]` community detection.
The one-scale structure of the *SCRS* has been reestablished in these results.

The combined rumination network shows a clear expected structure, with having high TPR for each sub-scale (on average, *brooding* (`r combined_tpr_s[1,2][[1]]`), *reflection* (`r combined_tpr_s[2,2][[1]]`) and *self-critical* (`r combined_tpr_s[3,2][[1]]`)).
Commenting on the stability of the network community structure the *RRS* *reflection* sub-scale exhibits strong TPR rates, and the weakness of the two items from their respective stand-alone network for items 2 and 9 are no longer present in the combined graph.
The *RRS* *brooding* scale has good separation in terms of TPR, except for its item 3 (*react*) having <0.9 TPR (*"Think Why do I always react this way?"*).
The one-scale SCRS has also a separable community with high (>0.925) TPR.
Keeping only the *spinglass* algoritm (as used by [@Bernstein2019]), we get high average 1.0 TPR for the combined graph.

Please refer to our vertex summary table in the Appendix (Table 3.) for actual descriptives, including expected influence, bridge node related statistics and average True Positive Rates for each vertex.
Please note where applicable, we used the standardized the scores.


### 3.2 Internal Structure with an exponential random graph model

In order to measure the impact of tools (*RRS*, *SCRS*) and their respective scales (*brooding*, *reflection* and *self-critical*) on network structure, we constructed an *exponential random graph model* (ERGM; @Hunter2007).
In the model of our combined network (predicting edges), *endogenous* predictors (related to the nature of the network structure) included the **number of edges** in the network (*edges* member), and a generalization of triadic structures based on alternating sums of *k-triangles* [@Hunter2007; @Goodreau2009] to involve some higher-order global network structures as a reflection on **clustering** in the form of completed triangles of vertices (we used *GWESP* (see @Goodreau2009), which stands for *geometrically weighted edgewise shared partner distribution*).
*GWESP* has the advantage of taking a parametric form of the shared common vertex count distribution on each edge, giving each connecting vertex a declining positive probability of two selected vertices being connected.
In order to capture *exogenous* effects (i.e., vertex attributes), we added *tool* and *sub-scale * as predictors, especially testing for *homophily* (assuming that belonging to the tool and its scale will increase the log-odds of being connected by an edge).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ergm_model_fit <- readRDS("output/ergmfit.RDS")
anova_tidy <- broom::tidy(anova(ergm_model_fit))
ergm_tidy <- broom::tidy(ergm_model_fit)
names(ergm_tidy) <- c("Term", "Estimate", "Std. Error", "MCMC Error %", "Statistic", "p")
ergm_tidy[2,1] <- 'GWESP [triangle]'
ergm_tidy[1,1] <- '# of edges'
ergm_tidy[3,1] <- 'Tool (main effect)'
ergm_tidy[4,1] <- 'Tool (homophily effect)'
ergm_tidy[5,1] <- 'Scale (homophily effect)'
goffit <- gof(ergm_model_fit)
get_p <- function(logit){
    exp(logit)/(1+exp(logit))
}

knitr::kable(ergm_tidy,digits=3,label="", caption="ERGM model fit results with Markov chain Monte Carlo Maximum Likelihood Estimation")



# gof(ergm_model_fit)
# mcmc.diagnostics(ergm_model_fit)
```

The model was built with *Markov chain Monte Carlo* (MCMC) maximum likelihood estimation (1000 iterations) to obtain model parameters by generating samples from the space of possible networks allowed by the data.


An ANOVA analysis on the overall model indicates (with df=`r anova_tidy$df[2][[1]]`, Residual Deviance=`r round(anova_tidy$Resid..Dev[2][[1]],3)`, p=`r round(anova_tidy$Pr...Chisq..[2][[1]],4)`) that variables involved in the model explain the network connectivity in a highly non-trivial fashion.
The detailed analysis reveals that *endogenous* effects such as the overall density of the network( number of *edges*) change the probability of the formation of an edge by `r round(get_p(ergm_tidy$Estimate[1][[1]]),3)`) and at p<0.05 level the closed triangle formulation (connectivity probability changed by `r round(get_p(ergm_tidy$Estimate)[2][[1]],3)`) indicates a non-trivial impact on clustering.
As expected, *exogenous* effects, such as two items belonging to the same sub-scale have a significant positive impact on connectivity (sub-scale changes edge probability by `r round(get_p(ergm_tidy$Estimate[5][[1]]),3)`, keeping the rest of the network fixed).
In terms of goodness-of-fit, observed frequencies of degree levels differ in non-significant manner from *MCMC*-simulated expectations.
In two cases (d=3 and d=6), the observed frequencies are above the simulated average (`r as.data.frame(goffit[18])[4,1]` > the expected avg. of`r as.data.frame(goffit[18])[4,3]` for d=3; and `r as.data.frame(goffit[18])[7,1]`  > the expected avg. of `r as.data.frame(goffit[18])[7,3]`  for d=6), but differences are not non-trivial.
Regarding the expected edgewise shares partners, the only deviation from expected levels it for 1 partner, where the observed frequency is 17 against 13.28.
Additional MCMC diagnostics revealed good fit of the model.

### 3.3 Association Network Inference

In order to test for non-zero edges in our network, we used a data-driven method to assess the null distribution of partial correlation coefficients used during network creation.
The R package **fdrtool** (@Strimmer2008) allowed us to model the probability density function $\eta_0$, the fraction of true null hypotheses in the data; and (1-$\eta_0$) for the true alternative hypotheses.
The mixture model for some statistic *S* thus takes the following form (where in our analysis, S is the partial correlation coefficient).

\begin{center}
$\ f(S)=\eta_0 f_0(S) + (1-\eta_0) f_1(S)$
\end{center}

To apply adjustment due to the number of performed tests, we applied the *False Discovery Rate* (FDR) to the *p*-values (the rate of false rejections against the number of rejections).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=6,fig.height=6, fig.align='center', fig.cap="Association Network Inference results"}
mute <- function(exp) {
  invisible(capture.output(exp))
}
mycorr <- cor_auto(rumi_data, detectOrdinal = TRUE)
mycorr <- cor(rumi_data, method = "spearman")
mycorr <- mycorr[upper.tri(mycorr)]
mute(fdr <- suppressWarnings(fdrtool(mycorr, statistic = "correlation", plot=FALSE)))
```
The low $\eta_0$ (`r round(unname(unlist(fdr['param'])[3]),3) `) indicates large mixing rate for the alternative hypothesis of edges having non-zero weights.
The histogram of absolute correlation coefficients estimated using the data (alternative component) has a centered shape in contrast to the null component.
The density-based FDR drops once empirical correlations reach $\rho$=0.1.



### 3.4 Latent Network Modeling

We constructed an *eigenmodel* to further explore the structure of the combined graph of *RRS* and *SCRS* (@Hoff2002; methodology following @Mair2018, @GaborCsardi2020) and how well the network structure predicts edge-formulation.
Our expectation was that sub-scales will have non-trivial impact on the resulting eigenvalues.
The model was built with the *eigenmodel_mcmc* function of the R package **eigenmodel**.
The function uses *Markov chain Monte Carlo* (MCMC) techniques to complete a model specification.
By applying eigenvalue decomposition, we obtained the first two eigenvectors and used them to plot the vertices (see Figure 2).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=10, fig.height=8, fig.cap="Vertices of the combined graph by the first two eigenvalues"}
fitEM <- readRDS("output/fitEM.RDS")
evals <- colMeans(fitEM$L_postsamp)
evecs <- eigen(fitEM$ULU_postmean)$vec[, 1:2]
subscale <- c("Brooding", "Reflection", "Brooding", "Reflection", "Reflection", "Brooding", "Brooding", "Brooding", "Reflection", "Reflection", rep("Self-critical", 10))
toolnames <- c(rep("RRS", 10), rep("SCRS", 10))
itemnames <- c(paste0("RRS_", 1:10), paste0("SCRS_", 1:10))
toollookup <- data.frame(item = V(rumi)$name, label = V(rumi)$label)
labels <- c()
for (item in seq_along(itemnames)) {
    label <- toollookup[toollookup$item == itemnames[item], ]$label
    item_name <- paste0(paste0(strsplit(itemnames[item],"_")[[1]], collapse="("),")")
    labels[item] <- paste0(item_name, "\n", label)
}
plot_eigen(evecs, evals, rumi_graph, toolnames, subscale, labels)
```

Our visual insight from *Figure 2.* is that the first eigenvector servers as a separator between *RRS* and *SCRS* having a posterior mean of $\bar{ev_1}$=`r round(evals[1],3)`.
The second eigenvector seems to separate between the upper half of the two-dimensional space of *SCRS* and the *brooding* scale, and the lower half being the *reflection* scale ($\bar{ev_2}$=`r round(evals[2],3)`).

In order to test the goodness-of-fit of the eigenmodel, using *k*-fold cross-validation (k=5), we refitted the model to a subset of the original data, using the complement 1/5 fraction for predicting the elements of the adjacency matrix of our original network.

For this part of the analysis, we defined three conditions in the *eigenmodel* on top of the original model.
In the first iteration we used the original *eigenmodel* (discussed above) without the regression component, defining the adjacency matrix as function of only the pairwise latent effects summarized in the following matrix.

\begin{center}
$\ Y_{ij}=f(u_i \Lambda u_j) $
\end{center}

In the second and third iterations, we defined an optional regression model in addition to the pairwise latent effects, where $\textbf{x}_{ij}$ is a pair-specific predictor vector.
This extends our model to the following equation.

\begin{center}
$\ Y_{ij}=f(\beta^{'} x_{ij} +  u_i \Lambda u_j) $
\end{center}

Thus, in the second iteration we cross-validated an extended *eigenmodel* with the **tool** (*RRS* or *SCRS*) as nominal grouping factor of vertices playing the predictor role.
And in the same manner, the third iteration tested a model with the scales of *brooding*, *reflection* and *self-critical* serving as pair-wise covariate predictor effects.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
A <- as_adjacency_matrix(rumi, sparse = FALSE)
Avec <- A[lower.tri(A)]
Avec.pred1 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred1.RDS")
Avec.pred2 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred2.RDS")
Avec.pred3 <- readRDS("/home/tamas/repos/rumination_lasso/output/Avecpred3.RDS")

getAUC <- function(x, condition) {
    y <- slot(x, "y.values")[[1]]
    x <- slot(x, "x.values")[[1]]
    Condition <- rep(condition, length(y))
    data.frame(x, y, Condition)
}

pred1 <- prediction(Avec.pred1, Avec)
perf1 <- performance(pred1, "tpr", "fpr")
pred2 <- prediction(Avec.pred2, Avec)
perf2 <- performance(pred2, "tpr", "fpr")
pred3 <- prediction(Avec.pred3, Avec)
perf3 <- performance(pred3, "tpr", "fpr")
# get AUC
aucs <- c()
for (v in c(pred1, pred2, pred3)) {
    auc <- performance(v, "auc")
    v <- slot(auc, "y.values")[[1]]
    aucs <- c(aucs, v)
}

```

Summarizing the results from the *eigenmodels*, using the original combined network adjacency matrix as a reference, we estimated the *Area Under the Curve* (AUC) statistics for each model.
Compared to the latent model ($\ AUC_{latent}$ =`r round(aucs[1], 3)`), the inclusion of the tool-level grouping factor resulted in a better predictive model ($\ AUC_{latent+tool}$ = `r round(aucs[2], 3)`).
The final model involving the scale-level vertex characteristics has the best goodness-of-fit ($\ AUC_{latent+scale}$ =`r round(aucs[3],3)`).
See Figure 4. in the Appendix for the corresponding ROC curves.

### 3.6 Network accuracy and stability

We used the *bootnet* R package to have an estimate of edge-weight accuracy with *non-parametric bootstrap* (2500 times sampling).
The resulting **accuracy** estimates have been visually incorporated in Figure 1 in the following manner.
Edge shade reflects the lower bound of the 95% confidence interval (CI) for each edge, while edges are presented with dashed line for cases of the CI including 0.0 edge weights.
For such cases,  we cannot be sure if their weight persist given different samples and varying sample characteristics.
Darker shaded, continuous edges are stable according to this bootstrap estimate and they preserve their sampled nature.
Cases like the relatively strong edge between *SCRS(5)* and *SCRS(7)* items indicate moderate penalized partial correlation between items in the SCRS network ($\rho$=`r round(E(SCRS_graph)[attributes(E(SCRS_graph))[1][[1]]=='SCRS_5|SCRS_7']$strength,3)`), but the edge is presented with dashed line and has lighter shade indicating a lower stability.
Examples for accurate and strong edges are *RRS(4)* (*alone1*; *"Go away by yourself and think about why you feel this way"*) and *RRS(10)* (*alone2*; *"Go someplace alone to think about your feelings"*). 
The edge weight for these items in their stand-alone *RRS* network is `r round(E(RRS_graph)[10]$strength,3)` (estimated edge-weight accuracy is with average `r round(accuracy_rrs[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(m) %>% unlist(),3)` with lower and upper CI bounds of `r round(accuracy_rrs[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(lower) %>% unlist(),3)` - `r round(accuracy_rrs[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(upper) %>% unlist(),3)`).
These items exhibit the same pattern in the combined network with estimated edge-weight accuracy with average weight of `r round(accuracy_combined[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(m) %>% unlist(),3)`; lower and upper CI bounds of `r round(accuracy_combined[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(lower) %>% unlist(),3)` - `r round(accuracy_combined[2][[1]]  %>% filter(node1=='RRS_4', node2=='RRS_10') %>% ungroup() %>%  dplyr::select(upper) %>% unlist(),3)`.

In the SCRS network we can track a *path* (a graph movement [*walk*] without repeated edges or vertices) between *SCRS* 6, 5, 9 and 10 items (please refer to Table 5. for edge-level weight and accuracy estimates of *SCRS*).

Such edges are less likely to exhibit similar characteristics with varying samples.

Network **stability** estimates for our three networks were carried out by using the *bootnet* function from the R package bearing the same name. 
We performed a *case dropping bootstrap* to simulate scenarios where fewer and fewer cases of the original sample would have been available and quantified the stability of the centrality metrics with the *Correlation Stability* (CS) coefficient. 
Bootstrap was performed with B=2500 resamples.

Accuracy and stability statistics have been summarized for *RRS*, *SCRS* and their combined graphs in respective tables of Appendix (see Table 4., 5. and 6).



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

RRS_stability <- readRDS("output/RRS_stability.RDS")
SCRS_stability <- readRDS("output/SCRS_stability.RDS")
combined_stability <- readRDS("output/combined_stability.RDS")

# edge_summary(rumi, accuracy_combined, combined_stability)
# edge_summary(RRS_graph, accuracy_rrs, RRS_stability)
# edge_summary(accuracy_scrs, SCRS_stability)


#CS estimates

# RRScorStab <-corStability(RRS_stability)
# saveRDS(RRScorStab, "output/RRScorStab.RDS")
# SCRScorStab <- corStability(SCRS_stability)
# saveRDS(SCRScorStab, "output/SCRScorStab.RDS")
# fullcorStab <- corStability(combined_stability)
# saveRDS(fullcorStab, "output/fullcorStab.RDS")

RRScorStab <- readRDS("output/RRScorStab.RDS")
SCRScorStab <- readRDS("output/SCRScorStab.RDS")
fullcorStab <- readRDS("output/fullcorStab.RDS")

CS_estimates <- tibble(RRS = round(RRScorStab,2),
       SCRS = round(SCRScorStab, 2),
       `RRS & SCRS` = round(fullcorStab,2))  %>% 
       as.data.frame()

rownames(CS_estimates) <- names(RRScorStab)

CS_estimates <- CS_estimates %>% 
  mutate(measure = rownames(CS_estimates)) %>% 
  select(Metric = measure, RRS, SCRS, `RRS & SCRS`)

CS_estimates <- as_tibble(CS_estimates)

```

As shown at [@Epskamp2017], the *Correlation Stability* coefficent is ideally between 0.25 and 0.5, the latter being the cut-off point for the estimate. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(CS_estimates, 
             caption = "Correlation Stability coefficient estimates for RRS, SCRS and their combined network", digits = 4)
```

Results indicate for betweenness centrality that neither networks tolerate much sample loss having CS-coefficients around 5% or lower.
For the *RRS* and *SCRS* graphs, the closeness metrics are stable in the sense that around `r round(CS_estimates[CS_estimates$Metric=='closeness','RRS'][[1]],2)*100`% and respectively `r round(CS_estimates[CS_estimates$Metric=='closeness','SCRS'][[1]],2)*100`% of the case can be dropped to still maintain 0.7 or higher correlation with their original estimates. 
The combined network's closeness stability is low and rigid.
Edge Weights exhibit a constant stability of `r round(CS_estimates[CS_estimates$Metric=='edge','RRS'][[1]],2)*100`%.
Edge Strength *Correlation Stability* coefficients are `r round(CS_estimates[CS_estimates$Metric=='strength','RRS'][[1]],2)*100`% (RRS), `r round(CS_estimates[CS_estimates$Metric=='strength','SCRS'][[1]],2)*100`% (SCRS) and `r round(CS_estimates[CS_estimates$Metric=='strength','RRS & SCRS'][[1]],2)*100`% (combined graph) which indicates increased tolerance for the combined network of the two questionnaires.

\newpage

## Discussion

In the present paper, we examined the separation of two facets of rumination (a generic one, moving on the *brooding*-*reflection* axis; and the *self-critical* aspects of rumination) using a network approach.
In accordance with our first hypothesis, in their respective network the Ruminative Response Style Questionnaire exhibits a two-scale structure. 
Our community detection estimates suggest though that the reflective aspects of rumination regarding analyzing one's self and strive to understand feelings (items 2 and 9 of *RRS*) have more to common with brooding, or emerge as a third aspect.
This latter concept is underlined by our eigenmodels, as in the two-dimensional space of the first two eigenvectors creates a separation between *RRS* and *SCRS* item in this fashion.
Items 2 and 9 are well separated even from the bulk of the rest of the RRS items.

Brooding has association with the self-critical aspects of rumination, which is highlighted by our eigenvector analysis as well as the sparse, unstable and weak edges with which reflection connects to brooding and self-critical rumination in their combined network.
In this scenario, we have gathered evidence of scale playing an important role in the edge-building process.
According to our exponential random graph model, indeed the internal factors of the combined network indeed have a non-trivial impact on associations in the network.
As shown, associations within the combined network only have low chances of false discovery.

Results indicate that network associations are accurate aligned to the internal factor structure (e.g., the items concerning the solitary nature of rumination), while some associations are more sensitive to sampling characteristics and sampling variation.
Edge strengths and edge weights have also high stability and relatively high resistance to sample loss, whereas betweenness is remarkably sensitive on our sample to any case-dropping.

\newpage
\blandscape

## Appendix

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(summary_table, format='simple', row.names=FALSE,caption="Network descriptive statistics for RRS, SCRS and their combined networks",label='Table 1',digits=2)
```

*Deg.=Degree; Str.=Strength; Bet.=Betweenness; Clo.=Closeness; EI1= One-step Expected Influence; EI2= Two-step Expected Influence; Br.Str.=Bridge Strength; Br.Bet.=Bridge Betweenness; Br.Cl.=Bridge Closeness; Br.EI1=One-step Bridge Expected Influence; Br.EI2=Two-step Bridge Expected Influence; TPR=average True Positive Rate*

\elandscape

\newpage


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE,fig.retina=1,fig.align='center', fig.width=10, fig.height=10, fig.cap='False Discovery Rate (FDR) for the combined network'}
mute(fdr <- suppressWarnings(fdrtool(mycorr, statistic = "correlation")))
```


\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(RRS_graph, accuracy_rrs,RRS_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the RRS network",label='Table 2',digits=2)
```

*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Edge Weight by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*

\elandscape
\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(SCRS_graph, accuracy_scrs,SCRS_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the SCRS network",label='Table 2',digits=2)
```


*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Edge Weight by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*

\elandscape
\newpage
\blandscape


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(edge_summary(rumi, accuracy_combined,combined_stability), format='simple', row.names=FALSE,caption="Edge Accuracy and Stability Statistics for the RRS and SCRS network",label='Table 2',digits=2)
```

*Vx.1=1st Vertex the edge attaches to; Vx.2=2nd Vertex the edge attaches to;Avg.Acc.=Average Edge Weight by Bootstrap; L.B.Acc.=Lower Bound of 95% CI for bootstrapped network accuracy; U.P.Acc.=Upper Bound of 95% CI for bootstrapped network accuracy; Statistic=type of network characteristic; Miss.%=Estimated average stability at the given missing rate of sample size*


\elandscape
\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE,fig.retina=1,fig.align='center', fig.width=10, fig.height=6, fig.cap='ROC curves of the combined RRS-SCRS network'}

ROC_data <- bind_rows(getAUC(perf1, "Latent effect"), getAUC(perf2, "Latent + Tool as pair-wise"), getAUC(perf3, "Latent + Scale as pair-wise"))

aucs_labels <- ""
conds <- c("Latent effect", "Latent + Tool", "Latent + Scale")
cond_lab <- ""

for (i in seq_along(conds)) {
    cond_lab <- paste0(cond_lab, conds[i], ":\n")
}

for (i in seq_along(conds)) {
    aucs_labels <- paste0(aucs_labels, round(aucs[i], 3), "\n")
}

means <- ROC_data %>% group_by(Condition) %>% summarize(x=mean(x), y=mean(y))
aucs_data <- tibble('Condition'= unique(ROC_data$Condition), 'AUC_value'=aucs) %>% left_join(means)
# ROC_data <- ROC_data %>% left_join(aucs_data)

ggplot(ROC_data, aes(x, y)) +
    geom_path(aes(x, y, group = Condition, color = Condition, linetype = Condition), size = 2) +
    geom_label(data=aucs_data, aes(x=rep(0.9, 3),y=c(0.4,0.5, 0.6),group=Condition,label=paste0(round(AUC_value,3)*100,'%'),fill=Condition), alpha=1/2)+
    scale_color_manual(values =c("#CA382A", "#0C38A0", "grey60")) +
    scale_fill_manual(values =c("#CA382A", "#0C38A0", "grey60")) +
    theme_bw() +
    labs(x = "False Positive Rate", y = "True Positive Rate") +
    # geom_rect(aes(xmin = 0.75, ymin = 0, xmax = 1.0, ymax = 0.25), fill = "white", color = "gray70") +
    theme(legend.position = "bottom")
```
\newpage
## References
