---
title: "Self-critical rumination - A network approach"
bibliography: rumination.bibtex
csl: apa7.csl
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# libraries declared
library(tidyverse)
library(networktools)
library(qgraph)
library(glasso)
library(ggraph)
library(igraph)
library(bootnet)
library(modelr)
library(scales)
library(knitr)
source("R/data_import.R")
source("R/functions.R")
# data import
source("../networks_with_r/get_rumi.R")
setwd('/home/tamas/repos/rumination_lasso')
```

## 2. Methods

### 2.1 Network analysis
*Psychological networks* have their own characteristics which differentiate them from other networks of the graph theory [@Epskamp2017; @Newman2010]. 
Nodes usually represent some psychological measures or items of a psychological assessment tool, while the edges of the network reflect the corresponding estimates of association derived from the data.
Having two rumination-related questionnaires, we assumed

* network analysis will reveal their respective internal structure previously established in the literature (RRS having a two-scale structure: reflection and brooding; while SCRS will show a single-scale structure);
* on the other hand, we hypothesized that in their common network, items overlapping in scope will change these clear outlines of the two measurement tools. According to our hypothesis, items of the RRS scale 'brooding' will have non-trivial association with the self-critical aspects of rumination;
* thus, we also assumed a combined rumination network, representing the generic (more trait-like) and the self-critical aspects of rumination will exhibit a three-component structure.

<!-- Sample sizes have direct impact on estimated accuracy and stability of the psychological network, thus the accuracy of the network parameters and measures is crucial: By obtaining robust results we can have a more realistic picture of a network without knowing the true network shape and structure. --> 
<!-- Just like any other psychological variables, network characteristics are also sensitive to sampling, estimation methods, included variables, outliers and various other components of an analysis. --> 
<!-- As [@Epskamp2017a] points out, psychological networks differ from *reflective latent variable models* by not seeking for a common cause of co-occurrence of variables (such as symptoms or different items of a questionnaire), but instead their focus is on quantifying and visually show the multivariate dependencies and the different pathways of direct relationships between the nodes. --> 
<!-- A major conceptual difference emerges from the network perspective for psychological data: psychological variables, such as symptoms, states, attitudes and other constructs (represented as nodes) have direct impact on each other, and are not caused by some latent variables.  [@Epskamp_2018]. --> 
In the current study, we used a fairly large sample of indiviuals (N=`r nrow(rumi_data)`) to construct a dense, undirected network of rumination-related psychological constructs. 
The vertices represent the items of the Ruminative Response Style (RRS) and the Self-critical Rumination Scale (SCRS), while edges are penalized partial correlations (using LASSO penalization, [@Friedman2007] ).


#### 2.1.1 Least Absolute Shrinkage and Selection Operator (LASSO)

We constructed individual and combined networks of RRS and SCRS with respective penalized correlation matrices using the *EBICglasso* function of the **qgraph** package (number of lambda parameters were set to 1000).
In order to shrink the edges, achieve high specificity, and get a less dense network, we let the function to exclude any elements of the underlying precision matrix below a threshold value (*threshold* parameter set to TRUE).

The LASSO uses L1 regularization([@Tibshirani1996], [@Friedman2007]), and in the current study, it results in a partial correlation network where edges represent direct associations between pairs of items, while the influence of all other items in the network are kept controlled. 
The regularization by L1 penalty ensures that trivially small partial correlations are set to zero [@McNally_2017], thus ensure a *sparse* network which are more interpretable (@Epskamp_2018). 

The tuning parameter of *gamma* in the graphical LASSO algorithm has been set to 0.5 value in accordance with [@McNally_2017] and [@Bernstein2019] in order to achieve sparse graphs. 
The final networks were chosen by the lowest values of the *extended Bayesian Information Criterion* (EBIC).

<!-- Before going further into network modeling, we estimated the 95% confidence intervals of network centrality measures to have an understanding of the sampling distribution of our estimates. According to @Epskamp2017a low sample size and non-regularized estimates might lead to amplify any bootstrap bias; by having a larger sample of individuals, we expect lesser levels of bias of any bootstrap estimates for network accuracy and stability. -->

#### 2.1.2 Goldbricker

We applied the *goldbricker* function from the R package *networktools* [@Jones2017] in order to search for pairs of items in the RRS, SCRS and their combined networks that were highly correlated (r > 0.75) and exhibited the same pattern with other items. 


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dataset <- rumi_data
var_names <- names(dataset)
```
After the LASSO regularization no further dimensionality reduction was necessary based upon the *goldbricker* evaluation.
As subject for this paper,


#### 2.1.3 Network descriptives
A comparative overview of the three networks was produced with their descriptives (degree distribution) and their centrality measures (strength, closeness, betweenness; [@GaborCsardi2020]), their One- and Two-Step Expected Influence (EI) measures ([@Robinaugh2016], [@Heeren2018]).
In order to further elaborate the question of vertex importance, we identified *bridge nodes* using the functions provided by the *networktools* R package [@Jones2017]. 
We estimated both one-step and two-step bridge expected influence measures which reflect the sum of edge weights connecting one vertex to other groups on vertices (or communities); and also express a vertex's secondary influence on the rest of the network, respectively. 
Higher influence scores indicate that a certain node is more likely to active neighbouring nodes, subgroups of nodes or communities.

#### 2.1.4. Community detection
In order to get an understanding of community of vertices and to see if vertices can be grouped into neighbourhoods corresponding to the previously established subscale-structure of RRS, SCRS and investigate their separation in their combined network, we used the community detection methods of the *igraph* R package. 
When detecting possible communities of vertices, we utilized previous insights [@Reichardt2006; @Bernstein2019, @GaborCsardi2020].

#### 2.1.6. Network accuracy and stability
Accuracy and stability have an important role in estimating network parameters when samples might vary in characteristics and size [@Epskamp2017; @Epskamp2017a]. One way of estimating network accuracy is to produce a 95% confidence interval of edge-weights with some variant of bootstrap. In our case we chose the non-parametric variant because of interpretability. Network stability is quantified with the *Correlation Stability* (CS-coefficient): an estimate of the maximum proportion of cases that can be dropped (with 95% certainty) to retain a correlation with the original centrality of higher than 0.7. Simulation studies [@Epskamp2017] show that the CS-coefficient should be between 0.25 and 0.5. 


 
## 3. Results

## 3.1.1. Network descriptives and internal structure (community detection) 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
i  <- 1000
# simulate_communities(RRS_graph, path="output/RRS_communities.RDS",i=i)
# simulate_communities(SCRS_graph, path="output/SCRS_communities.RDS",i=i)
# simulate_communities(rumi, path="output/combined_communities.RDS",i=i)
RRS_simulated_communities <- readRDS("output/RRS_communities.RDS")
SCRS_simulated_communities <- readRDS("output/SCRS_communities.RDS")
combined_simulated_communities <- readRDS("output/combined_communities.RDS")

# RRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# SCRS_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
# combined_simulated_communities  %>%
#     group_by(Item, Community)  %>%
#     summarize(N= n())
RRS_tpr <- suppressMessages(get_TPR(RRS_simulated_communities,RRS_graph))

RRS_tpr_s <- suppressMessages(RRS_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

SCRS_tpr <- suppressMessages(get_TPR(SCRS_simulated_communities,SCRS_graph))
SCRS_tpr_s <- suppressMessages(SCRS_tpr %>% 
    group_by(Subscale, Method, Weights)  %>%
    summarise(TPR_m = mean(TPR)))

combined_tpr <- suppressMessages(get_TPR(combined_simulated_communities,rumi))
combined_tpr_s <- suppressMessages(combined_tpr %>% 
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

as.data.frame(combined_tpr)
combined_tpr_top <- suppressMessages(combined_tpr %>% 
    filter(!Method %in% c("walktrap", "optimal","fast_greedy")) %>%
    group_by(Subscale)  %>%
    summarise(TPR_m = mean(TPR)))

for (seed in sample(1:100000,1000)) {
    set.seed(seed)
    weights <- TRUE
    method <- 'spinglass'
    summary_table <- bind_rows(network_summary(RRS_graph, name="RRS",seed=seed,method=method,weights=weights),
                                network_summary(SCRS_graph, name="SCRS", seed=seed,method=method,weights=weights),
                                network_summary(rumi, name="Combined RRS+SCRS",seed=seed,method=method,weights=weights))
}



```

The RRS (order of `r vcount(RRS_graph)`, size of `r ecount(RRS_graph)`) and SCRS (order of `r vcount(SCRS_graph)`, size of `r ecount(SCRS_graph)`) networks are densely connected relational networks.
While SCRS exhibits no *articulation point* (also call *cut vertex* whose removal would disconnect the network [@GaborCsardi2020]), the vertex of the *'problem'* item of RRS acts as an articulation point, as it would cut off the *'deserve'* vertex.
The combined network (order: `r vcount(rumi)`, size: `r ecount(rumi)`) has no articulation points neither.
In order to analyze their respective internal structures, we performed community detection using the *igraph* package in R.
As the choice of algorithm has non-trivial impact on the identified community structure, after having selected the *"optimal"*, the *"spinglass"*, the *"walktrap"* and (to also include hierarchical clustering) the *"fast greedy"* methods, we tested each a `r i` times on the three networks.
We also provided an edge weight vector in the form of the LASSO-penalized partial correlation coefficients (or alternatively, omitted weights).
The RRS two-scale structure could be recreated with all four algorithms with the inclusion of the weight vector not having effect on the measures.
For the subscale of *brooding* the average true positive rate was `r RRS_tpr_s[1,2][[1]]`.
In the case of *reflection*, TPR as `r round(RRS_tpr_s[2,2][[1]],3)`.

In the case of SCRS, the best TPR of `r SCRS_tpr_s[7,4][[1]]` has been achieved with `r SCRS_tpr_s[7,2][[1]]` community detection.
The SCRS exhibited a three-component structure according to community detection.

The combined rumination network shows a clear expected structure, with having high TPR for each subscale (on average, *brooding* (`r combined_tpr_s[1,2][[1]]`), *reflection* (`r combined_tpr_s[2,2][[1]]`) and *self-critical* (`r combined_tpr_s[3,2][[1]]`)).
Keeping only the *spinglass* algoritm (as used by [@Bernstein2019]), we get high 1.0 TPR.
Please refer to our summary table in the Appendix (Table 1.) for actual descriptives and identified communities using the *spinglass* method.

\newpage
\blandscape

## Appendix

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(summary_table, format='simple', row.names=FALSE,label="Network descriptive statistics for RRS, SCRS and their combined networks",digits=2)

```

\elandscape

\newpage

## References
