---
title: "Network Analysis on Rumination"
bibliography: rumination.bibtex
csl: apa7.csl
output:
  pdf_document: default
  html_document: default
---

```{r include = FALSE}
# libraries declared
library(tidyverse)
library(networktools)
library(qgraph)
library(glasso)
#library(ggraph)
library(igraph)
library(bootnet)
library(modelr)
library(scales)

```

```{r include = FALSE }

## color codes
global_colors <- tribble(
                         ~id, ~color,
                         1, "coral",
                         2, "cornflowerblue",
                         3, "snow3",
                         4, "seagreen3"
)

## global functions
standardize <- function(a) {
    est_mean <- mean(a, na.rm = TRUE)
    est_SD <- sd(a, na.rm = TRUE)

    (a - est_mean) / est_SD
}

tau_estimate <- function(x, y = NULL) {
  if (is.list(x)) {
    input <- x
    x <- input[[1]]
    y <- input[[2]]
  }

  concordants <- c()
  discordants <- c()
  total <- c(0)
  max_op <- length(x) * (length(y) - 1)
  for (index in seq(1, length(x))) {
    for (pair_index in seq(1, length(x))[!seq(1, length(x)) == index]) {
      first <- list(x[index], y[index])
      second <- list(x[pair_index], y[pair_index])
      if ((first[[1]] > second[[1]] & first[[2]] > second[[2]]) |
        (first[[1]] < second[[1]] & first[[2]] < second[[2]])) {
        concordants <- c(concordants, 1)
      } else {
        discordants <- c(discordants, -1)
      }
      total <- total + 1
      cat(paste0("\r", "Progress: ", round(total / max_op, 2) * 100, "%"))
    }
  }
  tau <- (sum(concordants) + sum(discordants)) / total
  if (is.nan(tau) & (length(x) == 1 | length(y) == 1)) {
    warning("Estimation not possible; input values are scalars")
  } else {
    cat(paste0("\n", "Tau estimate = ", tau))
  }
}

make_community_graph <- function(graph, covMatrix, labels) {
    igraph_converted <- as.igraph(graph, attributes = TRUE)
    group_estimation <- cluster_spinglass(
                                          igraph_converted,
                                          weights = NULL,
                                          vertex = NULL,
                                          spins = 25,
                                          parupdate = FALSE,
                                          start.temp = 1,
                                          stop.temp = 0.01,
                                          cool.fact = 0.99,
                                          update.rule = c("config", "random", "simple"),
                                          gamma = 0.5,
                                          implementation = c("orig", "neg"),
                                          gamma.minus = 1
    )


    grouping_order <- data.frame(id = group_estimation$membership) %>%
        left_join(global_colors) %>%
        select(color) %>%
        unlist()

    qgraph(covMatrix, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 530, theme = "TeamFortress", details = TRUE, threshold = FALSE, color = grouping_order, labels = labels)
}

find_tool <- function(itemname, data_labels) {
    if (str_locate(itemname, " .+ ")[1,1] > 0 & !is.na(str_locate(itemname, " .+ "))) {
        itemname <- str_sub(itemname, start = 1, end = str_locate(itemname, " .+ ")[1,1]-1)
    } else {
        itemname <- itemname
    }
    toolname <- data_labels[itemname == data_labels$labels, ]$var
    toolname <- str_sub(toolname, start = 1, end = str_locate(toolname, "_")[[1,1]] - 1)
    toolname
}
expected_inf_plot <- function(network, toolname) {
    influence_df <- networktools::expectedInf(network, step = c("both"), directed = FALSE)
    step1 <- unlist(influence_df["step1"])
    step2 <- unlist(influence_df["step2"])
    
    # z-scores
    step1_mean <- mean(step1, na.rm = TRUE)
    step1_sd <- sd(step1, na.rm = TRUE)
    step1 <- (step1 - step1_mean) / step1_sd
    step2_mean <- mean(step2, na.rm = TRUE)
    step2_sd <- sd(step2, na.rm = TRUE)
    step2 <- (step2 - step2_mean) / step2_sd
    
    varnames <- names(step1)
    varnames <- stringr::str_replace(varnames, "step1.","")
    for (i in seq_along(varnames)) {
        tool <- find_tool(varnames[i], data_labels)
        print(tool)
        varnames[i] <- paste0(tool, ": ", varnames[i])
    }
        influence_tibble <- tibble(
                               OneStep = step1,
                               TwoStep = step2,
                               item = factor(varnames, levels = varnames)) %>% 
    gather(1:2, key = Method, value = inf)

    influence_tibble %>%
        ggplot(aes(item, inf, group = Method, color = Method)) +
        geom_point(shape = 0, size = 2) +
        geom_path() +
        coord_flip() +
        scale_color_manual(values = global_colors$color[1:2]) +
        theme_light() +
        scale_x_discrete(limits = rev(levels(influence_tibble$item))) +
        labs(
             title = paste0("One- and Two-Step Expected Influence estimates for ", toolname),
             x = "Items",
             y = "Expected Influence (z-scores)"
             ) +
                         theme(
                               plot.title = element_text(size = 11)
                         )
}
make_bridge_plot <- function(network, toolname) {
    igraph_converted <- as.igraph(network, attributes = TRUE)
    group_estimation <- cluster_spinglass(
                                          igraph_converted,
                                          weights = NULL,
                                          vertex = NULL,
                                          spins = 25,
                                          parupdate = FALSE,
                                          start.temp = 1,
                                          stop.temp = 0.01,
                                          cool.fact = 0.99,
                                          update.rule = c("config", "random", "simple"),
                                          gamma = 0.5,
                                          implementation = c("orig", "neg"),
                                          gamma.minus = 1 )

#    community_vector <- c()
#    for (comm in seq_along(group_estimation[1:2])) {
#        comm_items <- c()
#        for (item in unlist(group_estimation[comm])) {
#            item <- c(item)
#            names(item) <- comm
#            comm_items <- c(comm_items, item)
#        }
#        community_vector <- c(community_vector, comm_items)
#    }
    if (length(unique(group_estimation$membership)) > 1) {
        bridge_estimate <- networktools::bridge(network, communities = group_estimation$membership)
    } else {
        bridge_estimate <- networktools::bridge(network)
    }

    # standardize scores into a tibble
    output_tibble <- tibble(.rows = length(bridge_estimate[[1]]))

    for (i in seq(1, 5)) {
        target_vector <- tibble(standardize(bridge_estimate[[i]]))
        colnames(target_vector) <- names(bridge_estimate)[i]
        output_tibble <- bind_cols(output_tibble, target_vector)
    }
    # add communities
    output_tibble <- bind_cols(output_tibble, bridge_estimate[6])
    output_tibble <- output_tibble[, names(bridge_estimate)]
    output_tibble <- output_tibble %>%
        mutate(item = names(bridge_estimate[[1]]))
    output_tibble <- output_tibble %>%
        mutate(Community = as_factor(communities))

    # reshape
    reshaped_output <- output_tibble %>%
        gather(1:5, key = measure, value = value)

    for (r in seq(1, nrow(reshaped_output))) {
        reshaped_output[r,"var"] <- find_tool(reshaped_output[r,"item"][[1]], data_labels)
        reshaped_output[r,"longitem"] <- paste0(reshaped_output[r, "var"], ": ", reshaped_output[r, "item"])

    }

    names(bridge_estimate[[1]]) <- unique(reshaped_output$longitem)
    


    # create plot

    reshaped_output %>%
        ggplot(aes(longitem, value, color = Community, shape = Community)) +
        geom_path(aes(group = measure), color = "black") +
        geom_point(size = 4) +
         coord_flip() +
         scale_color_manual(values = global_colors$color) +
         theme_light() +
         scale_x_discrete(limits = rev(levels(as_factor(names(bridge_estimate[[1]]))))) +
         facet_wrap(~measure, ncol = 5) +
         theme(
               legend.position = "bottom"
               ) +
                          labs(
                               x = "Item",
                               y = "Z-scores",
                               title = paste0("Bridge Expected Influence Estimates for ", toolname)
                               ) +
                          theme(
                                plot.title = element_text(size = 11)
                          )
}


network_accuracy_plot <- function(accuracy, tool = "", multiple=FALSE) {
    sample_data <- accuracy$sampleTable %>%
        filter(nchar(id)>7) %>%
        arrange(desc(value))
    
    sample_data <- sample_data %>%
    left_join(data_labels, by = c("node1" = "var")) %>%
    left_join(data_labels, by = c("node2" = "var")) %>% 
    rename(new_node_1 = labels.x,
           new_node_2 = labels.y) %>% 
        filter(!is.na(new_node_2)) %>% 
        mutate(tool1 = str_sub(node1, 1, str_locate(node1, "_")[,1] - 1),
               tool2 = str_sub(node2, 1, str_locate(node2, "_")[,1] - 1)) %>% 
        mutate(id = if_else(tool1 == tool2,
                            paste0(tool1, ": ", new_node_1, " - ", new_node_2),
                            paste0(tool1, ": ", new_node_1, " - ", tool2, ": ", new_node_2)))

    bootstrap_data_aggr <- accuracy$bootTable %>%
    left_join(data_labels, by = c("node1" = "var")) %>%
    left_join(data_labels, by = c("node2" = "var")) %>% 
    rename(new_node_1 = labels.x,
           new_node_2 = labels.y) %>% 
        filter(!is.na(new_node_2)) %>% 
        mutate(tool1 = str_sub(node1, 1, str_locate(node1, "_")[,1] - 1),
               tool2 = str_sub(node2, 1, str_locate(node2, "_")[,1] - 1)) %>% 
        mutate(id = if_else(tool1 == tool2,
                            paste0(tool1, ": ", new_node_1, " - ", new_node_2),
                            paste0(tool1, ": ", new_node_1, " - ", tool2, ": ", new_node_2))) %>% 
        filter(nchar(id)>7) %>%
        arrange(desc(value)) %>%
        group_by(id) %>%
        summarize(
                  m = mean(value, na.rm = TRUE),
                  lower = m - 1.96 * sd(value, na.rm = TRUE),
                  upper = m + 1.96 * sd(value, na.rm = TRUE)
        )


        
    bootstrap_data <- accuracy$bootTable %>%
        filter(nchar(id)>7) %>%
        arrange(desc(value))

    ggplot() +
        geom_vline(aes(xintercept = 0), linetype = "dotted", size = 0.75) +
        geom_point(data = bootstrap_data_aggr, aes(m, reorder(id, m)), shape = 22, fill = "cornflowerblue", size = 2) +
        geom_errorbar(data = bootstrap_data_aggr, aes(m, id, xmin = lower, xmax = upper), color = "cornflowerblue") +
        geom_point(data = sample_data, aes(value, reorder(id, value)), shape = 21, fill = "coral", size = 2) +
        theme_light() +
        labs(title = paste0("Edge Weight Accuracy Estimates with Bootstrap for ", tool),
             x = "Edge Weight",
             y = "Edge",
             caption = "DOT - the sample edge weight, SQUARE and confidence interval - the bootstrap estimates for edge weights (mean and 95% CI)") +
        scale_x_continuous(breaks = seq(-0.2, 0.8, 0.05))
}
```

## 2. Methods

### 2.1 Network analysis
*Psychological networks* have their own characteristics which differentiate them from other networks of the graph theory [@Epskamp2017; @Newman2010]. Nodes usually represent some psychological measures or items of a psychological assessment tool, the edges of the network reflect the corresponding estimates of association derived from the data. Sample sizes have direct impact on estimated accuracy and stability of the psychological network, thus the accuracy of the network parameters and measures is crucial: By obtaining robust results we can have a more realistic picture of a network without knowing the true network shape and structure. Just like any other psychological variables, network characteristics are also sensitive to sampling, estimation methods, included variables, outliers and various other components of an analysis. As [@Epskamp2017a] points out, psychological networks differ from *reflective latent variable models* by not seeking for a common cause of co-occurrence of variables (such as symptoms or different items of a questionnaire), but instead their focus is on quantifying and visually show the multivariate dependencies and the different pathways of direct relationships between the nodes.
In the current study, we used a fairly large sample as shown above. Before going further into network modeling, we estimated the 95% confidence intervals of network centrality measures to have an understanding of the sampling distribution of our estimates. According to @Epskamp2017a low sample size and non-regularized estimates might lead to amplify any bootstrap bias; by having a larger sample of individuals, we expect lesser levels of bias of any bootstrap estimates for network accuracy and stability.

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("~/repos/rumination_lasso/R/data_import.R")

var_names <- names(dataset)

RRS_items <- grep("RRS_[1,2,3,4,5,6,7,8,9,10]", var_names)
RRS_subset <- dataset[, RRS_items]
SCRS_items <- grep("SCRS_[1,2,3,4,5,6,7,8,9,10]", var_names)
SCRS_subset <- dataset[, SCRS_items]
ci_data  <- bind_cols(RRS_subset, SCRS_subset)



```

#### 2.1.1 Removing redundant items

As a preparation step, we applied the *goldbricker* function from the R package *networktools* to search for pairs of items in the RRS, SCRS and MHS items which were highly correlated (r > 0.50) and showed highly the same pattern with other items. When such "bad pairs" were identified, reduction techniques were put into use (with the *net_reduce* function in R): instead of the pair, the first principal component of the two variables were kept in the data as a new, merged variable.


```{r include = FALSE}

# sourcing the data import script to get the dataset as tibble
source("~/repos/rumination_lasso/R/data_import.R")

# 1. searching for highly correlated pairs of items [>.5]
var_names <- names(dataset)

#### RRS #####
RRS_items <- grep("RRS_[1,2,3,4,5,6,7,8,9,10]", var_names)
RRS_subset <- dataset[, RRS_items]

RRS_goldbricker <- goldbricker(RRS_subset, p = 0.05, method = "hittner2003", threshold = 0.25, corMin = 0.5, progressbar = TRUE)

# SCRS
SCRS_items <- grep("SCRS_[1,2,3,4,5,6,7,8,9,10]", var_names)
SCRS_subset <- dataset[, SCRS_items]

SCRS_goldbricker <- goldbricker(SCRS_subset, p = 0.05, method = "hittner2003", threshold = 0.25, corMin = 0.5, progressbar = TRUE)


# SCRS_goldbricker$proportion_matrix
suggested_SCRS <- SCRS_goldbricker$suggested_reductions
if (suggested_SCRS == "No suggested reductions") {
    SCRS_subset_reduced <- SCRS_subset
} else {
    SCRS_subset_reduced <- net_reduce(SCRS_subset, SCRS_goldbricker, method = c("PCA", "best_goldbricker"))
}

```

The RRS items required no reduction steps as the highly correlating items did not extend their pattern to more nodes (their correlations to other nodes did not violate the criteria that > 75% of these correlations did not differ significantly).

#### 2.1.2 Network Analysis with LASSO

For the network analysis, the tuning parameter of *gamma* in the grahical LASSO alogrithm has been set to 0.5 value in accordance with [@Bernstein2019] in order to achieve sparse graphs. The final networks were chosen by the lowest values of the *extended Bayesian Information Criterion* (EBIC).

#### 2.1.3. Community detection
In order to get an understanding of community of nodes and to see if nodes can be grouped into neighbourhoods, we used the *igraph* R package. When detecting possible communities of nodes, the detection happened with the following parameters in the *spinglass algorithm*:
TODO: try the walktrap algorithm from igraph!

#### 2.1.4. Expected Influence of nodes
To understand certain items' centrality and importance, besides regularly used centrality measures (such as strength, closeness and betweenness of nodes in a network), one can also use the One- and Two-Step Expected Influence (EI) measures [@robinaugh2016]. Traditionally in unweighted networks (where network edges are encoded to 0 or 1)  a node's centrality is the sum of edges, and in weighted nodes it is the sum of the edge weights. In this approach negative edges are treated the same way as positives, as the absolute values are used for centrality estimation. On the other hand, the Expected Influence metrics take into account if a node has positive and negative edges, too.

#### 2.1.5. Identifying important nodes
In order to further elaborate the question of node importance within the network, we identified *bridge nodes* using the functions provided by the *networktools* R package [@Jones2017]. We estimated both one-step and two-step bridge expected influence measures which reflect the sum of edge weights connecting one node to other groups on nodes (or communities of nodes); and also express a node's secondary influence on the rest of the network, respectively. Higher influence scores indicate that a certain node is more likely to active neighbouring nodes, subgroups of nodes or communities.


#### 2.1.6. Network accuracy and stability
Accuracy and stability have an important role in estimating network parameters when samples might vary in characteristics and size [@Epskamp2017]. One way of estimating network accuracy is to produce a 95% confidence interval of edge-weights with some variant of bootstrap. In our case we chose the nonparametric variant because of interpretability. Network stability is quantified with the *Correlation Stability* (CS-coefficient): an estimate of the maximum proportion of cases that can be dropped (with 95% certainty) to retain a correlation with the original centrality of higher than 0.7. Simulation studies [@Epskamp2017] show that the CS-coefficient should be between 0.25 and 0.5. 

#### 2.1.7. Difference Tests
In the final round of our analysis we estimated difference tests of network centrality indices and edge-weights to compare node importance. Difference tests are proposed by [@Epskamp2017]. These tests accomplish difference testing by using non-parametric bootstrap estimates of the centralities and edge-weights.
 
## 3. Results

### 3.1 Network plots
RSS network

```{r echo = FALSE, message = FALSE, warning = FALSE}

RRS_labels <- data_labels[grep("RRS", data_labels$var),]$labels
RRS_labels  <- RRS_labels[1:(length(RRS_labels)-3)]
RSScov2 <- qgraph::cor_auto(RRS_subset)
rss_network <- qgraph(RSScov2, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 530, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = RRS_labels)

#rss_network  <- estimateNetwork(RRS_subset, default="EBICglasso")
```


SCRS network
```{r echo = FALSE, message = FALSE, warning = FALSE}

SCRS_labels <- data_labels[grep("SCRS", data_labels$var),]$labels
SCRScov <- qgraph::cor_auto(SCRS_subset_reduced)
scrs_network <- qgraph(SCRScov, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 530, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = SCRS_labels)

#scrs_network  <- estimateNetwork(SCRS_subset, default="EBICglasso")
```

```{r echo = FALSE, message = FALSE, warning = FALSE}

# full data scenario
# MHC not included!
full_data <- dataset[, c(RRS_items, SCRS_items)] 
full_goldbricker <- goldbricker(full_data, p = 0.05, method = "hittner2003", threshold = 0.25, corMin = 0.5, progressbar = TRUE)
#full_goldbricker$suggested_reductions
full_reduced <- net_reduce(full_data, full_goldbricker, method = c("PCA", "best_goldbricker"))
full_cov <- qgraph::cor_auto(full_reduced)
full_labels  <- c(RRS_labels, SCRS_labels[c(3, 5, 6, 7, 9, 1)], "situation + sad", "mistakes + aspects")
full_network <- qgraph(full_cov, graph = "glasso", tuning = 0.5, layout = "spring", sampleSize = 888, theme = "TeamFortress", details = TRUE, threshold = FALSE, labels = full_labels)

```


### 3.2 Community detection 
Community mapping of RSS, MHC and SCRS with the *spinglass algorithm*:

RSS communities identified with parameters *gamma = 0.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*.

```{r echo = FALSE, message = FALSE, warning = FALSE}

make_community_graph(rss_network, RSScov2, RRS_labels)
```

SCRS communities identified with parameters *gamma = 0.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*.

```{r echo = FALSE, message = FALSE, warning = FALSE}

make_community_graph(scrs_network, SCRScov, SCRS_labels)
```


```{r echo = FALSE, message = FALSE, warning = FALSE}

# make_community_graph(MHC_network, MHCcov)

```

RRS and MHC combined communities identified with parameters *gamma = 0.5, spins = 25, starting temperature = 1, ending temperature = 0.01, cooling factor = 0.99*.

```{r echo = FALSE, message = FALSE, warning = FALSE}

make_community_graph(full_network, full_cov, full_labels)


```

### 3.3 Expected Influence
In order to estimate the Expected Influence metrics, we used the *expectedInf* function of the *networktools* R package. The influence score are standardized.


RRS Expected Influence Measures

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 5, fig.height=7}
expected_inf_plot(rss_network, "RRS")
```


```{r echo =FALSE, message = FALSE, warning = FALSE, fig.width = 5, fig.height=7}

# expected_inf_plot(MHC_network, "MHC")
```

SCRS Expected Influence Measures

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 5, fig.height=7}
expected_inf_plot(scrs_network, "SCRS")
```

Combined RRS and SCRS Expected Influence Measures

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 5, fig.height=7}
expected_inf_plot(full_network, "RRS & SCRS")
```

### 3.4 Bridge nodes

Using the *networktools* R library bridge expected influence measure were estimated for the three tools we used in this study. We also added aesthetics to reflect which items belonged to the same community according to our previous clustering steps.

RRS bridge estimates


```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height=4}
# get the estimate of bridge influence scores
make_bridge_plot(rss_network, "RRS")
```


SCRS bridge estimates


```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height=4}
make_bridge_plot(scrs_network, "SCRS")
```



```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height=4}
#make_bridge_plot(MHC_network, "MHC")
```

Combined RRS and SCRS bridge estimates


```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height=4}
make_bridge_plot(full_network, "RSS & SCRS")
```


### 3.5 Network accuracy and stability
We used the *bootnet* R package to have an estimate of edge-weight accuracy with *nonparametric bootstrap* (1000 times sampling) and also produce measures of centrality stability with *case dropping bootstrap* (to simulate cases where only the subset of the existing data would be available).


Network accuracy estimate for RRS

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10, fig.height=8}
# generate the accuracy estimate and save it
#RRS_network <- estimateNetwork(RRS_subset, default="EBICglasso")
#accuracy_rrs  <- bootnet(RRS_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_rrs, "../output/accuracy_rrs.RDS")

accuracy_rrs  <- readRDS("../output/accuracy_rrs.RDS")
network_accuracy_plot(accuracy_rrs, "RRS")
```



Network accuracy estimate for SCRS

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10, fig.height=8}
# generate the accuracy estimate and save it
#SCRS_network <- estimateNetwork(SCRS_subset, default="EBICglasso")
#accuracy_scrs  <- bootnet(SCRS_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_scrs, "../output/accuracy_scrs.RDS")

accuracy_scrs  <- readRDS("../output/accuracy_scrs.RDS")
network_accuracy_plot(accuracy_scrs, "SCRS")
```

Network accuracy estimate for combind RRS and SCRS

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.height=20}
# generate the accuracy estimate and save it
#combined_network <- estimateNetwork(full_data, default="EBICglasso")
#accuracy_combined  <- bootnet(combined_network, nBoots = 2500, cores = 6)
#saveRDS(accuracy_combined, "../output/accuracy_combined.RDS")

accuracy_combined  <- readRDS("../output/accuracy_combined.RDS")
network_accuracy_plot(accuracy_combined, "combined RRS and SCRS")
```


Network stability estimates for our three networks were carried out by using the *bootnet* function from the R package bearing the same name. We performed a *case dropping bootstrap* to simulate scenarios where fewer and fewer cases of the original sample would have been available and quantified the stability of the centrality metrics with the *Correlation Stability* (CS) coefficient. When estimating bootstrap, we set the number of bootstraps to 2500.

Stability for the RRS network

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.height=8}

#RRS_network <- estimateNetwork(RRS_subset, default="EBICglasso")
#RRS_stability <- bootnet(RRS_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(RRS_stability, "../output/RRS_stability.RDS")

#SCRS_network <- estimateNetwork(SCRS_subset, default="EBICglasso")
#SCRS_stability <- bootnet(SCRS_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(SCRS_stability, "../output/SCRS_stability.RDS")

#full_network <- estimateNetwork(full_data, default="EBICglasso")
#full_stability <- bootnet(full_network, nBoots = 2500, type="case", nCore = 6, statistics = c("strength", "betweenness", "closeness", "edge", "inStrength", "outStrength"), computeCentrality = TRUE)
#saveRDS(full_stability, "../output/full_stability.RDS")



#stability
RRS_stability <- readRDS("../output/RRS_stability.RDS")
SCRS_stability <- readRDS("../output/SCRS_stability.RDS")
full_stability <- readRDS("../output/full_stability.RDS")



network_stability_estimator <- function(network) {
    B_levels = seq(1, 2500)
    sample_data  <- t(matrix(network$sampleTable))
    names(sample_data) <- names(network$sampleTable)
    boot <- network$bootTable  %>%
        mutate(sample_rate = nPerson / mean(sample_data$nPerson)) %>%
        mutate(
               row = row_number(),
               bootstrap_indicator = (row %/% 75) + 1,
               bootstrap_indicator = factor(bootstrap_indicator, levels = B_levels))

    boot_data <- t(matrix(boot))
    names(boot_data) <- names(boot)

    drop_levels  <- unique(boot_data$nPerson)
    measures<- unique(sample_data$type)
    total_operations  <- 2500 * length(measures) * length(drop_levels)
    plot_data  <- matrix(ncol = 4, nrow = 0)
    colnames(plot_data) <- c("b", "measure", "level", "correlation")
    i = 0

    for (b in B_levels) {
        for (level in drop_levels) {
            for (m in measures) {
                i = i + 1
                
                boot_sample_bootstrap_mask  <- unlist(boot_data['bootstrap_indicator'], use.names=FALSE) == b
                boot_sample_level_mask  <- unlist(boot_data['nPerson'], use.names=FALSE) == level
                boot_sample_measure_mask  <- unlist(boot_data['type'], use.names=FALSE) == m
                boot_mask  <- boot_sample_bootstrap_mask & boot_sample_level_mask & boot_sample_measure_mask

                boot_sample <- unlist(boot_data['value'], use.names=FALSE)[boot_mask]


                original_sample_mask <- unlist(sample_data['type'], use.names=FALSE) == m
                original_sample <- unlist(sample_data['value'], use.names = FALSE)[original_sample_mask]

                test  <-all(!is.null(boot_sample), !is.null(original_sample), length(original_sample) == length(boot_sample)) 
                if (test) {
                    correlation = cor(boot_sample, original_sample)
                    new_record <- c(
                                         "b" = b,
                                         "measure" = m,
                                         "level" = level,
                                         "correlation" = correlation
                    )
                    plot_data <- rbind(plot_data, new_record)
                    cat(paste0("\rProgress: ", round((i/total_operations)*100,2), "%"))
                }
        }
    }
    }
    plot_df  <- tibble(as.data.frame(plot_data))
    plot_df  <- plot_df %>%
        mutate(level = as.numeric(level),
        correlation = as.numeric(correlation)) %>%
        group_by(b, measure) %>%
        summarise(r = mean(correlation, na.rm = TRUE),
                  sample_rate = level / max(unlist(sample_data['nPerson'], use.names = FALSE)))

    saveRDS(plot_df, paste0("../output/plot_", deparse(quote(network)), ".RDS"))

}

stability_estimate <- plot_RRS_stab
network_stability_plot <- function(stability_estimate){
    stability_estimate %>%
    mutate(b = as.numeric(b)) %>% 
        ggplot(aes(reorder(percent(sample_rate), desc(sample_rate)), r, group = measure)) +
        geom_point() +
        geom_hline(aes(yintercept = 0)) +
        geom_smooth(aes(color = measure, fill = measure), alpha = 1/4) +
      ylim(c(-1,1)) +
      theme_light() +
      scale_color_manual(values = c("coral4", "coral", "cornflowerblue", "darkturquoise"))+
      scale_fill_manual(values = c("coral4", "coral", "cornflowerblue", "darkturquoise"))+
      labs(x = "Portion of original sample",
           y = "Average correlation with the original sample") +
      #scale_x_continuous(breaks = seq(1.0, 0.0, -0.1)) +
      scale_y_continuous(breaks = seq(-1.0, 1.0, 0.1))

    
      
}

#CS estimates
RRScorStab <-corStability(RRS_stability)
SCRScorStab <- corStability(SCRS_stability)
fullcorStab <- corStability(full_stability)

CS_estimates <- tibble(RRS = RRScorStab,
       SCRS = SCRScorStab,
       combined = fullcorStab)

rownames(CS_estimates) <- names(RRScorStab)

CS_estimates <- CS_estimates %>% 
  mutate(measure = rownames(CS_estimates)) %>% 
  select(Metric = measure, RRS, SCRS, combined)
knitr::kable(CS_estimates, 
             caption = "Correlation Stability coefficient estimates for RRS, SCRS and their combined network", digits = 4)
```

As shown at [@Epskamp2017], the CS-coefficent is ideally between 0.25 and 0.5, the latter is the cat-off point for the estimate. The results show that RRS and SCRS closeness metrics are stable in the sense that around 28% of the case can be dropped to still maintain 0.7 or higher correlation with their original estimates. The closeness measure [`r CS_estimates[2, 4]`] for their combined network is already higher than the 0.5 cut-off. The same applies to all edge and strength estimates, with no regard of the network of RRS, SCRS or their combined variant. Betweenness measures are too low to be considered secure to interpret (all below 0.25) meaning that even slight case drops result in losing their stability.

### 3.6 Difference tests
The *bootnet* R package offers the *differenceTest* function to perform non-parametric bootstrap (bootstrapping with replacements). 

```{r echo = FALSE, message = FALSE, warning = FALSE}
RRS_network <- bootnet(RRS_subset, default="EBICglasso")
differenceTest()

plot_RRS_stab <- readRDS("../output/plot_RRS_stability.RDS")
network_stability_plot(plot_RRS_stab)
```


## References


